% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  11pt,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{5}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother





\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{adjustbox}
\usepackage{amsmath}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Address History Analysis: Eviction Persistence and Mover Trajectories},
  pdfauthor={Philly Evictions Project},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}


\title{Address History Analysis: Eviction Persistence and Mover
Trajectories}
\author{Philly Evictions Project}
\date{2026-03-04}
\begin{document}
\maketitle

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}

\section{Overview}\label{overview}

This document summarizes the address history analysis from
\texttt{r/address-history-analysis.R}. The script uses the InfoUSA
household panel to track tenants across moves and test whether exposure
to high-eviction buildings channels households into worse neighborhoods.

\textbf{Key questions:}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Do tenants from high-eviction buildings end up in other high-eviction
  buildings? (Eviction persistence)
\item
  What are the demographic characteristics of movers vs.~stayers?
\item
  Do tenants who move \emph{into} high-eviction buildings come from
  different neighborhoods? (Inflow)
\item
  Where do tenants go \emph{after} leaving high-eviction buildings?
  (Outflow)
\item
  Across a 3-move trajectory (origin \(\to\) middle \(\to\)
  destination), does passing through a high-evicting building shift
  tenants toward higher-eviction neighborhoods? (Trajectory analysis)
\end{enumerate}

\textbf{Unit of analysis:} Household (familyid) \(\times\) year panel,
with building-level (PID) characteristics merged in.

\textbf{Key data inputs:}

\begin{itemize}
\tightlist
\item
  \texttt{infousa\_cleaned} --- household-year panel with addresses
\item
  \texttt{infousa\_address\_xwalk} --- links InfoUSA addresses to parcel
  IDs
\item
  \texttt{bldg\_panel\_blp} --- building characteristics, filing rates,
  rents, occupancy
\item
  \texttt{infousa\_race\_imputed\_person},
  \texttt{infousa\_gender\_imputed\_person} --- demographic imputations
\end{itemize}

\section{Empirical Bayes Filing-Rate
Memo}\label{empirical-bayes-filing-rate-memo}

Main filing-intensity regressions in this writeup use
\texttt{filing\_rate\_eb\_pre\_covid} as the default building-level
eviction measure.

In the production pipeline (\texttt{r/make-analytic-sample.R}, section
\texttt{6b}), this is built as a Gamma-Poisson Empirical Bayes posterior
mean:

\[
y_{it} \mid \lambda_i \sim \text{Poisson}(E_{it}\lambda_i), \qquad
\lambda_i \sim \text{Gamma}(\alpha,\beta),
\]

with pooled pre-2019 sufficient statistics:

\[
Y_i = \sum_{t \le 2019} y_{it}, \qquad
E_i = \sum_{t \le 2019} E_{it},
\]

and posterior mean:

\[
\mathbb{E}[\lambda_i \mid Y_i, E_i] = \frac{\alpha + Y_i}{\beta + E_i}.
\]

City and ZIP priors are estimated by method-of-moments; ZIP priors fall
back to city prior when support is thin. Raw long-run filing-rate
results are kept as appendix robustness tables only.

\section{Data Construction}\label{data-construction}

\subsection{Rent Variables}\label{rent-variables}

The rent variable \texttt{med\_rent} is the coalesced value of Altos
median listing rent and eviction ongoing rent. The nominal log rent
\texttt{log\_med\_rent} is used for descriptive purposes.

For regression analysis, we construct a \textbf{hedonic-deflated real
rent} (\texttt{log\_med\_rent\_real}) by estimating a hedonic price
index. We estimate a weighted regression of log rent on year, building
type, and census tract fixed effects:

\[
\log(\text{rent}_{it}) = \alpha_t + \eta_k + \gamma_g + \varepsilon_{it}
\]

where \(\alpha_t\) are year fixed effects, \(\eta_k\) building type, and
\(\gamma_g\) census tract. The year FE \(\hat\alpha_t\) capture
aggregate rent inflation. Real rent is: \[
\log(\text{rent}^{\text{real}}_{it}) = \log(\text{rent}_{it}) - (\hat\alpha_t - \hat\alpha_{t_0})
\] where \(t_0\) is the earliest year in the sample.

\subsection{Filing Rate Variables}\label{filing-rate-variables}

Three filing rate measures are available:

\begin{itemize}
\tightlist
\item
  \textbf{\texttt{filing\_rate\_raw}}: Annual filings / occupied units.
  Year-varying, volatile, subject to small-denominator noise.
\item
  \textbf{\texttt{filing\_rate\_longrun\_pre2019}}: Total pre-2019
  filings / (total units \(\times\) years observed pre-2019).
  Time-invariant building-level average. Noisier for buildings with
  short panels.
\item
  \textbf{\texttt{filing\_rate\_eb\_pre\_covid}}: Empirical Bayes
  shrinkage estimator (Gamma-Poisson model), pre-2019, city-wide prior.
  Time-invariant. Shrinks noisy short-panel rates toward the city mean.
\end{itemize}

Main-text filing regressions use \texttt{filing\_rate\_eb\_pre\_covid}.
Raw long-run filing-rate regressions
(\texttt{filing\_rate\_longrun\_pre2019}) are reported in the appendix
for robustness.

\section{Tracking Descriptives}\label{tracking-descriptives}

\subsection{Movers vs.~Stayers}\label{movers-vs.-stayers}

The script identifies rental households and classifies them as
\emph{movers} (2+ addresses over the panel) or \emph{stayers} (1
address). Summary statistics are computed for each group.

\begin{table}[htbp]
\centering
\centering
\caption{Tracking Descriptives: Movers vs.\ Stayers}
\label{tab:tracking_descriptives}

\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{lrrr}
\toprule
 & All Rental HHs & Stayers (1 address) & Movers (2+ addresses) \\
\midrule
N HH-Years & 4,527,988 & 3,627,712 &   900,276 \\
N Unique HHs & 1,180,429 & 1,102,507 &    77,922 \\
Mean Addresses per HH & 1.21 & 1 & 4.12 \\
Mean Years Observed & 3.47 & 3.29 & 5.97 \\
\% Black (mean posterior) & 34.3 & 34.2 & 34.9 \\
\% White (mean posterior) & 57.1 & 56.9 & 58.6 \\
\% Hispanic (mean posterior) & 5.7 & 5.8 & 5 \\
\% Female HoH & 55 & 54.2 & 61.5 \\
Mean Filing Rate & 0.0692 & 0.0742 & 0.0492 \\
Mean Building Size (units) & 22.8 & 22.5 & 24 \\
Mean Log Rent & 7.159 & 7.139 & 7.231 \\
N Unique Tracts & 418 & 415 & 402 \\
\bottomrule
\end{tabular}

\end{adjustbox}
\end{table}

\section{Eviction Persistence
Regressions}\label{eviction-persistence-regressions}

\subsection{Setup}\label{setup}

The core persistence analysis asks: conditional on a household
\emph{moving}, does the eviction filing rate at their \textbf{previous}
building predict the filing rate at their \textbf{current} building?

\textbf{Sample:} Rental-to-rental movers (both origin and current
address are rental buildings). Filing rates are pre-COVID,
time-invariant building characteristics (not annual rates).

\subsection{Regression Specifications}\label{regression-specifications}

The persistence regressions estimate: \[
\text{FilingRate}^{EB}_{i,\text{dest}} = \beta \cdot \text{FilingRate}^{EB}_{i,\text{origin}} + \gamma' X_i + \alpha_{\text{tract,dest}} + \alpha_{\text{tract,orig}} + \varepsilon_i
\] where \(\text{FilingRate}^{EB}\) is the EB shrinkage filing rate,
\(X_i\) includes hedonic-deflated real rent at origin and destination,
and \(\alpha_{\text{tract}}\) are census tract fixed effects (used
instead of block group to avoid over-absorption with building-level
time-invariant rates). Standard errors are clustered by destination PID.

\textbf{Specifications:}

\begin{itemize}
\tightlist
\item
  \textbf{m1} (bivariate): Filing rate at destination \(\sim\) filing
  rate at origin
\item
  \textbf{m2} (+ FE): Add unit bin and census tract fixed effects
  (current and previous)
\item
  \textbf{m3} (+ real rent): Add hedonic-deflated log rent at origin and
  destination
\end{itemize}

Raw long-run versions of these same specs are shown in the appendix.

\begin{table}[htbp]
\centering
\caption{\label{tab:evict_persist} Eviction Persistence: EB Shrinkage Filing Rates (Main)}
\centering

\begin{adjustbox}{max width=\textwidth}
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variable: & \multicolumn{3}{c}{Filing rate (destination, EB)}\\
                                           & m1             & m2             & m3 \\   
      Model:                               & (1)            & (2)            & (3)\\  
      \midrule
      \emph{Variables}\\
      Filing rate (origin, EB)             & 0.1063$^{***}$ & 0.0486$^{***}$ & 0.0442$^{***}$\\   
                                           & (0.0137)       & (0.0086)       & (0.0101)\\   
      Avg real rent (destination building) &                &                & -0.0594$^{***}$\\   
                                           &                &                & (0.0029)\\   
      Avg real rent (origin building)      &                &                & 0.0006\\   
                                           &                &                & (0.0029)\\   
      \midrule
      \emph{Fixed-effects}\\
      Units bin (destination)              &                & Yes            & Yes\\  
      Units bin (origin)                   &                & Yes            & Yes\\  
      Destination tract FE                 &                & Yes            & Yes\\  
      Origin tract FE                      &                & Yes            & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                         & 87,910         & 87,897         & 56,361\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (pid) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}

\end{adjustbox}
\end{table}

\subsection{High-Filer and Rent
Regressions}\label{high-filer-and-rent-regressions}

The high-filer regressions use a binary indicator (\(\ge 15\%\) EB
filing rate) in place of the continuous rate:

\begin{itemize}
\tightlist
\item
  \textbf{m4}: High-filer (dest) \(\sim\) high-filer (origin) + FE
\item
  \textbf{m5}: Add hedonic-deflated rent controls, restrict to
  multi-unit buildings
\item
  \textbf{m\_rent}: Real rent (dest) \(\sim\) filing rate (origin) +
  real rent (origin) + filing rate (dest) + FE
\end{itemize}

\begin{table}[htbp]
\centering
\caption{\label{tab:evict_persist_hf_rent} High-Filer Persistence and Rent Regressions (EB Main)}
\centering

\begin{adjustbox}{max width=\textwidth}
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variables: & \multicolumn{2}{c}{high\_filing\_dest} & Avg real rent (destination building)\\
                                           & m4             & m5              & m\_rent \\    
      Model:                               & (1)            & (2)             & (3)\\  
      \midrule
      \emph{Variables}\\
      high\_filing\_origTRUE               & 0.0566$^{***}$ & 0.0690$^{***}$  &   \\   
                                           & (0.0049)       & (0.0114)        &   \\   
      Avg real rent (destination building) &                & -0.0677$^{***}$ &   \\   
                                           &                & (0.0170)        &   \\   
      Avg real rent (origin building)      &                & -0.0021         & 0.2186$^{***}$\\   
                                           &                & (0.0062)        & (0.0071)\\   
      Filing rate (origin, EB)             &                &                 & -0.0182$^{**}$\\   
                                           &                &                 & (0.0075)\\   
      Filing rate (destination, EB)        &                &                 & -0.2619$^{***}$\\   
                                           &                &                 & (0.0353)\\   
      \midrule
      \emph{Fixed-effects}\\
      Units bin (destination)              & Yes            & Yes             & Yes\\  
      Units bin (origin)                   & Yes            & Yes             & Yes\\  
      Destination tract FE                 & Yes            & Yes             & Yes\\  
      Origin tract FE                      & Yes            & Yes             & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                         & 87,897         & 20,186          & 56,361\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (pid) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}

\end{adjustbox}
\end{table}

\section{Inflow and Outflow Analysis}\label{inflow-and-outflow-analysis}

\subsection{Leave-One-Out Tract Eviction
Rate}\label{leave-one-out-tract-eviction-rate}

For each building, the LOO tract eviction rate is:

\[
\text{LOO}_{i} = \frac{\sum_{j \in \text{tract}(i), j \neq i} \text{filings}_{j}}{\sum_{j \in \text{tract}(i), j \neq i} \text{unit-years}_{j}}
\]

This measures the eviction environment of the building's neighborhood,
excluding the building's own contribution.

\subsection{Eviction Intensity Bins}\label{eviction-intensity-bins}

Buildings are classified using the empirical Bayes eviction filing rate
(pre-COVID):

\begin{longtable}[]{@{}ll@{}}
\toprule\noalign{}
Bin & Definition \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
{[}0,1) & EB rate \(\in [0, 0.01)\) \\
{[}1,5) & EB rate \(\in [0.01, 0.05)\) \\
{[}5,10) & EB rate \(\in [0.05, 0.10)\) \\
{[}10,20) & EB rate \(\in [0.10, 0.20)\) \\
{[}20,inf) & EB rate \(\ge 0.20\) \\
\end{longtable}

\subsection{Inflow: Where Do Tenants at High-Eviction Buildings Come
From?}\label{inflow-where-do-tenants-at-high-eviction-buildings-come-from}

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{llrrrrrr}
\caption{\label{tab:inflow-table}Origin characteristics of movers, by destination eviction intensity}\\
\toprule
Destination bin & N moves & Origin \% Black & Dest \% Black & Origin LOO evict & Dest LOO evict & Mover \% Black & Mover \% Female\\
\midrule
{}[0,1) & 51,525 & 0.327 & 0.331 & 0.0390 & 0.0388 & 0.247 & 0.588\\
{}[1,5) & 8,215 & 0.280 & 0.276 & 0.0356 & 0.0377 & 0.176 & 0.571\\
{}[5,10) & 12,252 & 0.480 & 0.497 & 0.0526 & 0.0549 & 0.448 & 0.630\\
{}[10,20) & 10,109 & 0.505 & 0.523 & 0.0563 & 0.0587 & 0.480 & 0.645\\
{}[20,inf) & 5,879 & 0.578 & 0.569 & 0.0643 & 0.0732 & 0.547 & 0.663\\
\bottomrule
\end{longtable}
\endgroup{}

\subsection{Outflow: Where Do Tenants From High-Eviction Buildings
Go?}\label{outflow-where-do-tenants-from-high-eviction-buildings-go}

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{llrrrrr}
\caption{\label{tab:outflow-table}Destination characteristics of movers, by origin eviction intensity}\\
\toprule
Origin bin & N moves & Origin LOO evict & Dest LOO evict & \$\textbackslash{}Delta\$ LOO tract & Mover \% Black & Mover \% Female\\
\midrule
{}[0,1) & 49,277 & 0.0376 & 0.0405 & 0.0029 & 0.255 & 0.583\\
{}[1,5) & 8,759 & 0.0337 & 0.0333 & -0.0004 & 0.157 & 0.572\\
{}[5,10) & 13,103 & 0.0519 & 0.0533 & 0.0014 & 0.416 & 0.636\\
{}[10,20) & 10,813 & 0.0573 & 0.0568 & -0.0005 & 0.468 & 0.646\\
{}[20,inf) & 6,191 & 0.0725 & 0.0658 & -0.0067 & 0.547 & 0.664\\
\bottomrule
\end{longtable}
\endgroup{}

\section{Three-Move Trajectory
Analysis}\label{three-move-trajectory-analysis}

\subsection{Design}\label{design}

The trajectory analysis tracks households across three consecutive
residential spells:

\[
\text{Origin} \xrightarrow{\text{move 1}} \text{Middle} \xrightarrow{\text{move 2}} \text{Destination}
\]

The key question: conditional on origin neighborhood, does the eviction
intensity of the \textbf{middle} building predict worse outcomes at the
\textbf{destination} building?

\textbf{Primary filing outcomes} use building-level EB filing rates
directly, capturing within-neighborhood sorting:

\begin{itemize}
\tightlist
\item
  \(\Delta\text{FR}^{\text{EB}} = \text{FR}^{\text{EB}}_{\text{dest}} - \text{FR}^{\text{EB}}_{\text{origin}}\)
  (change in EB filing rate)
\end{itemize}

Raw long-run filing-rate versions are reported in the appendix as
robustness checks.

\textbf{Secondary outcome} uses the LOO tract eviction rate
(neighborhood-level, excluding the focal building): \[
\Delta\text{LOO} = \text{LOO}_{\text{dest}} - \text{LOO}_{\text{origin}}
\]

The LOO rate averages over all buildings in the tract and thus misses
within-tract sorting --- a tenant moving between two high-eviction
buildings in the same tract shows zero change in LOO. Building-level
rates capture this directly.

\subsection{Descriptive Summary}\label{descriptive-summary}

\begingroup\fontsize{9}{11}\selectfont

\begin{longtable}[t]{llrrrrrrrrr}
\caption{\label{tab:trajectory-table}Three-move trajectories by middle building eviction intensity}\\
\toprule
Middle bin & N traj. & Orig EB & Dest EB & \$\textbackslash{}Delta\$ EB & Orig LOO (EB) & Dest LOO (EB) & \$\textbackslash{}Delta\$ LOO (EB) & Orig LOO (raw) & Dest LOO (raw) & \$\textbackslash{}Delta\$ LOO (raw)\\
\midrule
{}[0,1) & 104,812 & 0.0381 & 0.0398 & 0.0017 & 0.0491 & 0.0492 & 2e-04 & 0.0436 & 0.0435 & -1e-04\\
{}[1,5) & 9,196 & 0.0417 & 0.0406 & -0.0011 & 0.0451 & 0.0453 & 2e-04 & 0.0422 & 0.0416 & -5e-04\\
{}[5,10) & 23,030 & 0.0544 & 0.0552 & 0.0008 & 0.0578 & 0.0582 & 4e-04 & 0.0510 & 0.0509 & -1e-04\\
{}[10,20) & 16,075 & 0.0643 & 0.0672 & 0.0029 & 0.0604 & 0.0609 & 5e-04 & 0.0533 & 0.0533 & 0e+00\\
{}[20,inf) & 7,037 & 0.0930 & 0.0991 & 0.0061 & 0.0652 & 0.0656 & 4e-04 & 0.0580 & 0.0578 & -2e-04\\
\bottomrule
\end{longtable}
\endgroup{}

\subsection{Trajectory Regressions}\label{trajectory-regressions}

For each outcome family, the script estimates delta and
destination-level models separately, with progressively richer origin
conditioning. Filing-outcome models are estimated using both:

\begin{itemize}
\tightlist
\item
  middle-building filing bins (\texttt{{[}0,1)}, \texttt{{[}1,5)},
  \texttt{{[}5,10)}, \texttt{{[}10,20)}, \texttt{{[}20,inf)})
\item
  a high-filing dummy
  (\texttt{\textbackslash{}ge\ 15\textbackslash{}\%})
\end{itemize}

\textbf{Delta specs:}

\textbf{(A) Unconditional delta:} \[
\Delta Y_i = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b] + \varepsilon_i
\]

\textbf{(B) Delta + origin tract FE:} \[
\Delta Y_i = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b] + \alpha_{\text{tract,orig}} + \varepsilon_i
\]

\textbf{(C) Delta + origin filing rate + origin parcel controls:} \[
\Delta Y_i = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b]
 + \theta Y_{\text{orig},i}
 + \gamma' X_{\text{orig},i}
 + \alpha_{\text{tract,orig}} + \varepsilon_i
\]

\textbf{(D) Delta + origin-tract-by-origin-filing-bin FE:} \[
\Delta Y_i = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b]
 + \gamma' X_{\text{orig},i}
 + \alpha_{\text{tract,orig} \times \text{orig\_filing\_bin}} + \varepsilon_i
\]

\textbf{Destination-level specs:}

\textbf{(A) Destination level + origin tract FE:} \[
Y_{\text{dest},i} = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b] + \alpha_{\text{tract,orig}} + \varepsilon_i
\]

\textbf{(B) + origin outcome level:} \[
Y_{\text{dest},i} = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b] + \theta Y_{\text{orig},i} + \alpha_{\text{tract,orig}} + \varepsilon_i
\]

\textbf{(C) + origin parcel controls:} \[
Y_{\text{dest},i} = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b]
 + \theta Y_{\text{orig},i}
 + \gamma' X_{\text{orig},i}
 + \alpha_{\text{tract,orig}} + \varepsilon_i
\]

\textbf{(D) + origin-tract-by-origin-filing-bin FE:} \[
Y_{\text{dest},i} = \sum_{b} \beta_b \cdot \mathbf{1}[\text{mid\_bin}_i = b]
 + \gamma' X_{\text{orig},i}
 + \alpha_{\text{tract,orig} \times \text{orig\_filing\_bin}} + \varepsilon_i
\]

where \(Y\) is one of: building-level filing rate, severe complaints per
unit, total violations per unit, severe violations per unit, or LOO
tract filing rate (EB or raw). Origin parcel controls
\(X_{\text{orig},i}\) include \texttt{log(total\_area)},
\texttt{log(market\_value)}, \texttt{year\_blt\_decade},
\texttt{num\_units\_bin}, \texttt{building\_type},
\texttt{quality\_grade\_standard}, and \texttt{num\_stories\_bin}.
Reference category for bin models: {[}0,1). Standard errors are
clustered by origin block group.

\subsubsection{Filing Outcomes: Delta Specs
(Primary)}\label{filing-outcomes-delta-specs-primary}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Change in filing rate (destination - origin, EB)}\\
                                                  & Delta A        & Delta B       & Delta C         & Delta D \\   
   Model:                                         & (1)            & (2)           & (3)             & (4)\\  
   \midrule
   \emph{Variables}\\
   Constant                                       & 0.0017$^{***}$ &               &                 &   \\   
                                                  & (0.0003)       &               &                 &   \\   
   Middle building filing-rate bin $=$ [1,5)")    & -0.0028$^{*}$  & -0.0030$^{*}$ & 0.0017          & 0.0022$^{*}$\\   
                                                  & (0.0017)       & (0.0017)      & (0.0011)        & (0.0012)\\   
   Middle building filing-rate bin $=$ [5,10)")   & -0.0009        & -0.0004       & 0.0048$^{***}$  & 0.0043$^{***}$\\   
                                                  & (0.0010)       & (0.0010)      & (0.0007)        & (0.0008)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0012         & 0.0018        & 0.0135$^{***}$  & 0.0121$^{***}$\\   
                                                  & (0.0013)       & (0.0013)      & (0.0010)        & (0.0012)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0044$^{*}$   & 0.0053$^{**}$ & 0.0364$^{***}$  & 0.0297$^{***}$\\   
                                                  & (0.0026)       & (0.0026)      & (0.0022)        & (0.0025)\\   
   Origin filing rate (EB)                        &                &               & -0.9401$^{***}$ &   \\   
                                                  &                &               & (0.0079)        &   \\   
   Log(origin total area)                         &                &               & 0.0030$^{***}$  & -0.0003\\   
                                                  &                &               & (0.0007)        & (0.0009)\\   
   Log(origin market value)                       &                &               & -0.0071$^{***}$ & -0.0098$^{***}$\\   
                                                  &                &               & (0.0015)        & (0.0019)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                &                & Yes           & Yes             & \\  
   Origin year-built decade FE                    &                &               & Yes             & Yes\\  
   Origin unit-bin FE                             &                &               & Yes             & Yes\\  
   Origin building-type FE                        &                &               & Yes             & Yes\\  
   Origin quality-grade FE                        &                &               & Yes             & Yes\\  
   Origin stories-bin FE                          &                &               & Yes             & Yes\\  
   Origin tract x origin filing-bin FE            &                &               &                 & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,137        & 160,132       & 157,330         & 157,262\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Filing Outcomes: Destination-Level Specs
(Primary)}\label{filing-outcomes-destination-level-specs-primary}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Destination filing rate (EB)}\\
                                                  & Dest A         & Dest B         & Dest C          & Dest D \\   
   Model:                                         & (1)            & (2)            & (3)             & (4)\\  
   \midrule
   \emph{Variables}\\
   Middle building filing-rate bin $=$ [1,5)")    & 0.0055$^{***}$ & 0.0049$^{***}$ & 0.0017          & 0.0024$^{**}$\\   
                                                  & (0.0011)       & (0.0011)       & (0.0011)        & (0.0011)\\   
   Middle building filing-rate bin $=$ [5,10)")   & 0.0068$^{***}$ & 0.0063$^{***}$ & 0.0048$^{***}$  & 0.0048$^{***}$\\   
                                                  & (0.0009)       & (0.0008)       & (0.0007)        & (0.0008)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0163$^{***}$ & 0.0153$^{***}$ & 0.0135$^{***}$  & 0.0129$^{***}$\\   
                                                  & (0.0011)       & (0.0010)       & (0.0010)        & (0.0010)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0442$^{***}$ & 0.0416$^{***}$ & 0.0364$^{***}$  & 0.0341$^{***}$\\   
                                                  & (0.0026)       & (0.0024)       & (0.0022)        & (0.0021)\\   
   Origin filing rate (EB)                        &                & 0.0688$^{***}$ & 0.0599$^{***}$  &   \\   
                                                  &                & (0.0089)       & (0.0079)        &   \\   
   Log(origin total area)                         &                &                & 0.0030$^{***}$  & 0.0026$^{***}$\\   
                                                  &                &                & (0.0007)        & (0.0007)\\   
   Log(origin market value)                       &                &                & -0.0071$^{***}$ & -0.0063$^{***}$\\   
                                                  &                &                & (0.0015)        & (0.0014)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                & Yes            & Yes            & Yes             & \\  
   Origin year-built decade FE                    &                &                & Yes             & Yes\\  
   Origin unit-bin FE                             &                &                & Yes             & Yes\\  
   Origin building-type FE                        &                &                & Yes             & Yes\\  
   Origin quality-grade FE                        &                &                & Yes             & Yes\\  
   Origin stories-bin FE                          &                &                & Yes             & Yes\\  
   Origin tract x origin filing-bin FE            &                &                &                 & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,132        & 160,132        & 157,330         & 157,262\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Filing Outcomes: Destination-Level Specs (High-Filing
Dummy,
Primary)}\label{filing-outcomes-destination-level-specs-high-filing-dummy-primary}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Destination filing rate (EB)}\\
                                                   & Dest A         & Dest B         & Dest C          & Dest D \\   
   Model:                                          & (1)            & (2)            & (3)             & (4)\\  
   \midrule
   \emph{Variables}\\
   Middle building high-filing indicator (>=15\%)  & 0.0312$^{***}$ & 0.0292$^{***}$ & 0.0258$^{***}$  & 0.0242$^{***}$\\   
                                                   & (0.0018)       & (0.0017)       & (0.0015)        & (0.0014)\\   
   Origin filing rate (EB)                         &                & 0.0711$^{***}$ & 0.0615$^{***}$  &   \\   
                                                   &                & (0.0091)       & (0.0080)        &   \\   
   Log(origin total area)                          &                &                & 0.0030$^{***}$  & 0.0027$^{***}$\\   
                                                   &                &                & (0.0007)        & (0.0007)\\   
   Log(origin market value)                        &                &                & -0.0073$^{***}$ & -0.0065$^{***}$\\   
                                                   &                &                & (0.0015)        & (0.0015)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                 & Yes            & Yes            & Yes             & \\  
   Origin year-built decade FE                     &                &                & Yes             & Yes\\  
   Origin unit-bin FE                              &                &                & Yes             & Yes\\  
   Origin building-type FE                         &                &                & Yes             & Yes\\  
   Origin quality-grade FE                         &                &                & Yes             & Yes\\  
   Origin stories-bin FE                           &                &                & Yes             & Yes\\  
   Origin tract x origin filing-bin FE             &                &                &                 & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                    & 160,132        & 160,132        & 157,330         & 157,262\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Severe Complaints per Unit: Delta Specs (Additional
Outcome)}\label{severe-complaints-per-unit-delta-specs-additional-outcome}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Change in severe complaints per unit}\\
                                                  & Delta A               & Delta B       & Delta C         & Delta D \\   
   Model:                                         & (1)                   & (2)           & (3)             & (4)\\  
   \midrule
   \emph{Variables}\\
   Constant                                       & $8.02\times 10^{-5}$  &               &                 &   \\   
                                                  & (0.0034)              &               &                 &   \\   
   Middle building filing-rate bin $=$ [1,5)")    & -0.0041               & -0.0078       & -0.0105         & -0.0272\\   
                                                  & (0.0162)              & (0.0166)      & (0.0121)        & (0.0176)\\   
   Middle building filing-rate bin $=$ [5,10)")   & -0.0169               & -0.0128       & 0.0158$^{*}$    & 0.0047\\   
                                                  & (0.0116)              & (0.0120)      & (0.0092)        & (0.0121)\\   
   Middle building filing-rate bin $=$ [10,20)")  & -0.0132               & -0.0080       & 0.0492$^{***}$  & 0.0247$^{*}$\\   
                                                  & (0.0139)              & (0.0142)      & (0.0110)        & (0.0143)\\   
   Middle building filing-rate bin $=$ [20,inf)") & -0.0433$^{*}$         & -0.0382$^{*}$ & 0.0558$^{***}$  & 0.0302\\   
                                                  & (0.0225)              & (0.0228)      & (0.0166)        & (0.0237)\\   
   Origin severe complaints per unit              &                       &               & -0.9584$^{***}$ &   \\   
                                                  &                       &               & (0.0040)        &   \\   
   Log(origin total area)                         &                       &               & 0.0144$^{*}$    & -0.0504$^{***}$\\   
                                                  &                       &               & (0.0082)        & (0.0117)\\   
   Log(origin market value)                       &                       &               & 0.0043          & -0.0196$^{*}$\\   
                                                  &                       &               & (0.0094)        & (0.0115)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                &                       & Yes           & Yes             & \\  
   Origin year-built decade FE                    &                       &               & Yes             & Yes\\  
   Origin unit-bin FE                             &                       &               & Yes             & Yes\\  
   Origin building-type FE                        &                       &               & Yes             & Yes\\  
   Origin quality-grade FE                        &                       &               & Yes             & Yes\\  
   Origin stories-bin FE                          &                       &               & Yes             & Yes\\  
   Origin tract x origin filing-bin FE            &                       &               &                 & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,284               & 160,279       & 157,468         & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Severe Complaints per Unit: Destination-Level Specs
(Additional
Outcome)}\label{severe-complaints-per-unit-destination-level-specs-additional-outcome}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Destination severe complaints per unit}\\
                                                  & Dest A         & Dest B         & Dest C         & Dest D \\   
   Model:                                         & (1)            & (2)            & (3)            & (4)\\  
   \midrule
   \emph{Variables}\\
   Middle building filing-rate bin $=$ [1,5)")    & -0.0154        & -0.0150        & -0.0105        & -0.0054\\   
                                                  & (0.0119)       & (0.0119)       & (0.0121)       & (0.0122)\\   
   Middle building filing-rate bin $=$ [5,10)")   & 0.0197$^{**}$  & 0.0182$^{**}$  & 0.0158$^{*}$   & 0.0148\\   
                                                  & (0.0091)       & (0.0091)       & (0.0092)       & (0.0093)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0527$^{***}$ & 0.0500$^{***}$ & 0.0492$^{***}$ & 0.0494$^{***}$\\   
                                                  & (0.0110)       & (0.0109)       & (0.0110)       & (0.0111)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0648$^{***}$ & 0.0603$^{***}$ & 0.0558$^{***}$ & 0.0553$^{***}$\\   
                                                  & (0.0168)       & (0.0167)       & (0.0166)       & (0.0167)\\   
   Origin severe complaints per unit              &                & 0.0439$^{***}$ & 0.0416$^{***}$ &   \\   
                                                  &                & (0.0039)       & (0.0040)       &   \\   
   Log(origin total area)                         &                &                & 0.0144$^{*}$   & 0.0175$^{**}$\\   
                                                  &                &                & (0.0082)       & (0.0084)\\   
   Log(origin market value)                       &                &                & 0.0043         & 0.0044\\   
                                                  &                &                & (0.0094)       & (0.0098)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                & Yes            & Yes            & Yes            & \\  
   Origin year-built decade FE                    &                &                & Yes            & Yes\\  
   Origin unit-bin FE                             &                &                & Yes            & Yes\\  
   Origin building-type FE                        &                &                & Yes            & Yes\\  
   Origin quality-grade FE                        &                &                & Yes            & Yes\\  
   Origin stories-bin FE                          &                &                & Yes            & Yes\\  
   Origin tract x origin filing-bin FE            &                &                &                & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,279        & 160,279        & 157,468        & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Total Violations per Unit: Delta Specs (Additional
Outcome)}\label{total-violations-per-unit-delta-specs-additional-outcome}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Change in total violations per unit}\\
                                                  & Delta A  & Delta B  & Delta C         & Delta D \\   
   Model:                                         & (1)      & (2)      & (3)             & (4)\\  
   \midrule
   \emph{Variables}\\
   Constant                                       & 0.0104   &          &                 &   \\   
                                                  & (0.0154) &          &                 &   \\   
   Middle building filing-rate bin $=$ [1,5)")    & -0.0237  & -0.0366  & -0.0505         & -0.1696$^{**}$\\   
                                                  & (0.0674) & (0.0688) & (0.0538)        & (0.0747)\\   
   Middle building filing-rate bin $=$ [5,10)")   & -0.0787  & -0.0654  & 0.0673          & 0.0045\\   
                                                  & (0.0546) & (0.0559) & (0.0413)        & (0.0562)\\   
   Middle building filing-rate bin $=$ [10,20)")  & -0.0100  & 0.0101   & 0.2734$^{***}$  & 0.1270$^{*}$\\   
                                                  & (0.0666) & (0.0677) & (0.0530)        & (0.0680)\\   
   Middle building filing-rate bin $=$ [20,inf)") & -0.0644  & -0.0479  & 0.2546$^{***}$  & 0.1695$^{*}$\\   
                                                  & (0.0935) & (0.0950) & (0.0768)        & (0.0987)\\   
   Origin total violations per unit               &          &          & -0.9445$^{***}$ &   \\   
                                                  &          &          & (0.0040)        &   \\   
   Log(origin total area)                         &          &          & -0.0871$^{**}$  & -0.3360$^{***}$\\   
                                                  &          &          & (0.0342)        & (0.0520)\\   
   Log(origin market value)                       &          &          & 0.0685          & 0.1933$^{***}$\\   
                                                  &          &          & (0.0421)        & (0.0584)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                &          & Yes      & Yes             & \\  
   Origin year-built decade FE                    &          &          & Yes             & Yes\\  
   Origin unit-bin FE                             &          &          & Yes             & Yes\\  
   Origin building-type FE                        &          &          & Yes             & Yes\\  
   Origin quality-grade FE                        &          &          & Yes             & Yes\\  
   Origin stories-bin FE                          &          &          & Yes             & Yes\\  
   Origin tract x origin filing-bin FE            &          &          &                 & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,284  & 160,279  & 157,468         & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Total Violations per Unit: Destination-Level Specs
(Additional
Outcome)}\label{total-violations-per-unit-destination-level-specs-additional-outcome}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Destination total violations per unit}\\
                                                  & Dest A         & Dest B         & Dest C         & Dest D \\   
   Model:                                         & (1)            & (2)            & (3)            & (4)\\  
   \midrule
   \emph{Variables}\\
   Middle building filing-rate bin $=$ [1,5)")    & -0.0809        & -0.0783        & -0.0505        & -0.0388\\   
                                                  & (0.0530)       & (0.0525)       & (0.0538)       & (0.0541)\\   
   Middle building filing-rate bin $=$ [5,10)")   & 0.0873$^{**}$  & 0.0781$^{*}$   & 0.0673         & 0.0680\\   
                                                  & (0.0417)       & (0.0415)       & (0.0413)       & (0.0416)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.2879$^{***}$ & 0.2711$^{***}$ & 0.2734$^{***}$ & 0.2785$^{***}$\\   
                                                  & (0.0532)       & (0.0527)       & (0.0530)       & (0.0540)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.2606$^{***}$ & 0.2420$^{***}$ & 0.2546$^{***}$ & 0.2513$^{***}$\\   
                                                  & (0.0771)       & (0.0761)       & (0.0768)       & (0.0777)\\   
   Origin total violations per unit               &                & 0.0604$^{***}$ & 0.0555$^{***}$ &   \\   
                                                  &                & (0.0039)       & (0.0040)       &   \\   
   Log(origin total area)                         &                &                & -0.0871$^{**}$ & -0.0676$^{*}$\\   
                                                  &                &                & (0.0342)       & (0.0351)\\   
   Log(origin market value)                       &                &                & 0.0685         & 0.0507\\   
                                                  &                &                & (0.0421)       & (0.0443)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                & Yes            & Yes            & Yes            & \\  
   Origin year-built decade FE                    &                &                & Yes            & Yes\\  
   Origin unit-bin FE                             &                &                & Yes            & Yes\\  
   Origin building-type FE                        &                &                & Yes            & Yes\\  
   Origin quality-grade FE                        &                &                & Yes            & Yes\\  
   Origin stories-bin FE                          &                &                & Yes            & Yes\\  
   Origin tract x origin filing-bin FE            &                &                &                & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,279        & 160,279        & 157,468        & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Severe Violations per Unit: Delta Specs (Additional
Outcome)}\label{severe-violations-per-unit-delta-specs-additional-outcome}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Change in severe violations per unit}\\
                                                  & Delta A  & Delta B  & Delta C         & Delta D \\   
   Model:                                         & (1)      & (2)      & (3)             & (4)\\  
   \midrule
   \emph{Variables}\\
   Constant                                       & -0.0013  &          &                 &   \\   
                                                  & (0.0048) &          &                 &   \\   
   Middle building filing-rate bin $=$ [1,5)")    & 0.0014   & -0.0039  & 0.0049          & -0.0159\\   
                                                  & (0.0190) & (0.0195) & (0.0163)        & (0.0213)\\   
   Middle building filing-rate bin $=$ [5,10)")   & -0.0188  & -0.0121  & 0.0134          & 0.0009\\   
                                                  & (0.0173) & (0.0176) & (0.0118)        & (0.0177)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0066   & 0.0132   & 0.0401$^{***}$  & 0.0373$^{*}$\\   
                                                  & (0.0189) & (0.0195) & (0.0144)        & (0.0198)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0209   & 0.0289   & 0.0668$^{***}$  & 0.0787$^{**}$\\   
                                                  & (0.0306) & (0.0312) & (0.0253)        & (0.0321)\\   
   Origin severe violations per unit              &          &          & -0.9867$^{***}$ &   \\   
                                                  &          &          & (0.0038)        &   \\   
   Log(origin total area)                         &          &          & -0.0100         & -0.0270$^{**}$\\   
                                                  &          &          & (0.0089)        & (0.0119)\\   
   Log(origin market value)                       &          &          & 0.0164          & 0.0042\\   
                                                  &          &          & (0.0118)        & (0.0168)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                &          & Yes      & Yes             & \\  
   Origin year-built decade FE                    &          &          & Yes             & Yes\\  
   Origin unit-bin FE                             &          &          & Yes             & Yes\\  
   Origin building-type FE                        &          &          & Yes             & Yes\\  
   Origin quality-grade FE                        &          &          & Yes             & Yes\\  
   Origin stories-bin FE                          &          &          & Yes             & Yes\\  
   Origin tract x origin filing-bin FE            &          &          &                 & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,284  & 160,279  & 157,468         & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{Severe Violations per Unit: Destination-Level Specs
(Additional
Outcome)}\label{severe-violations-per-unit-destination-level-specs-additional-outcome}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Destination severe violations per unit}\\
                                                  & Dest A         & Dest B         & Dest C         & Dest D \\   
   Model:                                         & (1)            & (2)            & (3)            & (4)\\  
   \midrule
   \emph{Variables}\\
   Middle building filing-rate bin $=$ [1,5)")    & 0.0112         & 0.0110         & 0.0049         & 0.0072\\   
                                                  & (0.0155)       & (0.0155)       & (0.0163)       & (0.0165)\\   
   Middle building filing-rate bin $=$ [5,10)")   & 0.0162         & 0.0157         & 0.0134         & 0.0132\\   
                                                  & (0.0117)       & (0.0117)       & (0.0118)       & (0.0118)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0433$^{***}$ & 0.0428$^{***}$ & 0.0401$^{***}$ & 0.0406$^{***}$\\   
                                                  & (0.0143)       & (0.0143)       & (0.0144)       & (0.0146)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0728$^{***}$ & 0.0722$^{***}$ & 0.0668$^{***}$ & 0.0662$^{***}$\\   
                                                  & (0.0253)       & (0.0252)       & (0.0253)       & (0.0256)\\   
   Origin severe violations per unit              &                & 0.0152$^{***}$ & 0.0133$^{***}$ &   \\   
                                                  &                & (0.0038)       & (0.0038)       &   \\   
   Log(origin total area)                         &                &                & -0.0100        & -0.0099\\   
                                                  &                &                & (0.0089)       & (0.0091)\\   
   Log(origin market value)                       &                &                & 0.0164         & 0.0148\\   
                                                  &                &                & (0.0118)       & (0.0124)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                & Yes            & Yes            & Yes            & \\  
   Origin year-built decade FE                    &                &                & Yes            & Yes\\  
   Origin unit-bin FE                             &                &                & Yes            & Yes\\  
   Origin building-type FE                        &                &                & Yes            & Yes\\  
   Origin quality-grade FE                        &                &                & Yes            & Yes\\  
   Origin stories-bin FE                          &                &                & Yes            & Yes\\  
   Origin tract x origin filing-bin FE            &                &                &                & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,279        & 160,279        & 157,468        & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{LOO Tract Filing Rate Outcomes (EB, Secondary
Main)}\label{loo-tract-filing-rate-outcomes-eb-secondary-main}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccccc}
   \tabularnewline \midrule \midrule
   Dependent Variables: & \multicolumn{2}{c}{Change in LOO tract filing rate (EB)} & \multicolumn{4}{c}{Destination LOO tract filing rate (EB)}\\
                                                  & Delta A                & Delta B        & Dest A         & Dest B         & Dest C                & Dest D \\   
   Model:                                         & (1)                    & (2)            & (3)            & (4)            & (5)                   & (6)\\  
   \midrule
   \emph{Variables}\\
   Constant                                       & 0.0002                 &                &                &                &                       &   \\   
                                                  & (0.0002)               &                &                &                &                       &   \\   
   Middle building filing-rate bin $=$ [1,5)")    & $-1.31\times 10^{-5}$  & 0.0002         & 0.0002         & 0.0002         & 0.0002                & 0.0002\\   
                                                  & (0.0003)               & (0.0003)       & (0.0003)       & (0.0003)       & (0.0003)              & (0.0002)\\   
   Middle building filing-rate bin $=$ [5,10)")   & 0.0002                 & 0.0008$^{***}$ & 0.0007$^{***}$ & 0.0007$^{***}$ & 0.0007$^{***}$        & 0.0007$^{***}$\\   
                                                  & (0.0002)               & (0.0001)       & (0.0001)       & (0.0001)       & (0.0001)              & (0.0001)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0003                 & 0.0011$^{***}$ & 0.0010$^{***}$ & 0.0010$^{***}$ & 0.0010$^{***}$        & 0.0010$^{***}$\\   
                                                  & (0.0002)               & (0.0002)       & (0.0002)       & (0.0002)       & (0.0002)              & (0.0002)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0002                 & 0.0016$^{***}$ & 0.0011$^{***}$ & 0.0013$^{***}$ & 0.0013$^{***}$        & 0.0014$^{***}$\\   
                                                  & (0.0004)               & (0.0003)       & (0.0003)       & (0.0003)       & (0.0003)              & (0.0003)\\   
   Origin LOO tract filing rate (EB)              &                        &                &                & 0.3713$^{**}$  & 0.3631$^{**}$         &   \\   
                                                  &                        &                &                & (0.1508)       & (0.1619)              &   \\   
   Log(origin total area)                         &                        &                &                &                & $3.81\times 10^{-5}$  & $4.12\times 10^{-5}$\\    
                                                  &                        &                &                &                & (0.0002)              & (0.0002)\\   
   Log(origin market value)                       &                        &                &                &                & -0.0007$^{***}$       & -0.0007$^{***}$\\   
                                                  &                        &                &                &                & (0.0002)              & (0.0002)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                &                        & Yes            & Yes            & Yes            & Yes                   & \\  
   Origin year-built decade FE                    &                        &                &                &                & Yes                   & Yes\\  
   Origin unit-bin FE                             &                        &                &                &                & Yes                   & Yes\\  
   Origin building-type FE                        &                        &                &                &                & Yes                   & Yes\\  
   Origin quality-grade FE                        &                        &                &                &                & Yes                   & Yes\\  
   Origin stories-bin FE                          &                        &                &                &                & Yes                   & Yes\\  
   Origin tract x origin filing-bin FE            &                        &                &                &                &                       & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,667                & 160,658        & 160,658        & 160,658        & 157,691               & 157,563\\  
   \midrule \midrule
   \multicolumn{7}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{7}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsubsection{LOO Tract Filing Rate Outcomes (EB High-Filing Dummy,
Secondary
Main)}\label{loo-tract-filing-rate-outcomes-eb-high-filing-dummy-secondary-main}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccccc}
   \tabularnewline \midrule \midrule
   Dependent Variables: & \multicolumn{2}{c}{Change in LOO tract filing rate (EB)} & \multicolumn{4}{c}{Destination LOO tract filing rate (EB)}\\
                                                   & Delta A  & Delta B        & Dest A         & Dest B         & Dest C                & Dest D \\   
   Model:                                          & (1)      & (2)            & (3)            & (4)            & (5)                   & (6)\\  
   \midrule
   \emph{Variables}\\
   Constant                                        & 0.0002   &                &                &                &                       &   \\   
                                                   & (0.0002) &                &                &                &                       &   \\   
   Middle building high-filing indicator (>=15\%)  & 0.0002   & 0.0012$^{***}$ & 0.0009$^{***}$ & 0.0010$^{***}$ & 0.0010$^{***}$        & 0.0011$^{***}$\\   
                                                   & (0.0003) & (0.0002)       & (0.0002)       & (0.0002)       & (0.0002)              & (0.0002)\\   
   Origin LOO tract filing rate (EB)               &          &                &                & 0.3694$^{**}$  & 0.3615$^{**}$         &   \\   
                                                   &          &                &                & (0.1508)       & (0.1619)              &   \\   
   Log(origin total area)                          &          &                &                &                & $4.22\times 10^{-5}$  & $4.34\times 10^{-5}$\\    
                                                   &          &                &                &                & (0.0002)              & (0.0002)\\   
   Log(origin market value)                        &          &                &                &                & -0.0007$^{***}$       & -0.0008$^{***}$\\   
                                                   &          &                &                &                & (0.0002)              & (0.0002)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                 &          & Yes            & Yes            & Yes            & Yes                   & \\  
   Origin year-built decade FE                     &          &                &                &                & Yes                   & Yes\\  
   Origin unit-bin FE                              &          &                &                &                & Yes                   & Yes\\  
   Origin building-type FE                         &          &                &                &                & Yes                   & Yes\\  
   Origin quality-grade FE                         &          &                &                &                & Yes                   & Yes\\  
   Origin stories-bin FE                           &          &                &                &                & Yes                   & Yes\\  
   Origin tract x origin filing-bin FE             &          &                &                &                &                       & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                    & 160,667  & 160,658        & 160,658        & 160,658        & 157,691               & 157,563\\  
   \midrule \midrule
   \multicolumn{7}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{7}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\section{Interpretation}\label{interpretation}

\textbf{Eviction persistence:} The positive coefficient on previous
filing rate indicates that tenants who leave high-eviction buildings
tend to end up in other high-eviction buildings, even after controlling
for tract and building size. This is not simply a neighborhood effect,
and persists within origin-tract conditioning. EB is the main measure
shown; raw long-run robustness is in the appendix.

\textbf{Hedonic rent deflation:} Using hedonic-deflated real rents
(rather than nominal) ensures that rent persistence results are not
confounded by aggregate rent inflation over the panel period. The year
fixed effects from the hedonic regression capture common rent trends, so
\texttt{log\_med\_rent\_real} isolates cross-sectional and
within-building rent variation.

\textbf{Inflow/Outflow:} High-eviction buildings draw tenants from
neighborhoods that are already higher-eviction, and their departing
tenants move to similar or worse neighborhoods. The LOO tract eviction
rate captures the neighborhood environment excluding the focal building.

\textbf{Trajectories:} The trajectory design reports delta and
destination-level outcomes separately, and adds richer origin
conditioning (origin filing rate, origin parcel controls, and
origin-tract-by-origin-filing-bin FE). This clarifies whether sorting
patterns persist after conditioning on baseline origin-building risk and
building characteristics. We also add severe complaints per unit as an
additional long-run building-level outcome. Unlike the LOO measure,
building-level outcomes capture within-neighborhood sorting, so tenants
may systematically sort into worse buildings even within the same tract.

\section{Appendix: Raw Filing
Robustness}\label{appendix-raw-filing-robustness}

\subsection{Persistence (Raw Long-Run Filing
Rate)}\label{persistence-raw-long-run-filing-rate}

\begin{table}[htbp]
\centering
\caption{\label{tab:evict_persist_raw} Eviction Persistence: Raw Long-Run Filing Rates (Appendix Robustness)}
\centering

\begin{adjustbox}{max width=\textwidth}
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variable: & \multicolumn{3}{c}{Filing rate (destination, raw long-run)}\\
                                           & m1             & m2             & m3 \\   
      Model:                               & (1)            & (2)            & (3)\\  
      \midrule
      \emph{Variables}\\
      Filing rate (origin, raw long-run)   & 0.1069$^{***}$ & 0.0466$^{***}$ & 0.0447$^{***}$\\   
                                           & (0.0162)       & (0.0092)       & (0.0114)\\   
      Avg real rent (destination building) &                &                & -0.0599$^{***}$\\   
                                           &                &                & (0.0028)\\   
      Avg real rent (origin building)      &                &                & 0.0016\\   
                                           &                &                & (0.0029)\\   
      \midrule
      \emph{Fixed-effects}\\
      Units bin (destination)              &                & Yes            & Yes\\  
      Units bin (origin)                   &                & Yes            & Yes\\  
      Destination tract FE                 &                & Yes            & Yes\\  
      Origin tract FE                      &                & Yes            & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                         & 87,989         & 87,976         & 56,412\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (pid) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}

\end{adjustbox}
\end{table}

\subsection{High-Filer and Rent (Raw Long-Run Filing
Rate)}\label{high-filer-and-rent-raw-long-run-filing-rate}

\begin{table}[htbp]
\centering
\caption{\label{tab:evict_persist_hf_rent_raw} High-Filer Persistence and Rent Regressions (Raw Long-Run Appendix Robustness)}
\centering

\begin{adjustbox}{max width=\textwidth}
   \begin{tabular}{lccc}
      \tabularnewline \midrule \midrule
      Dependent Variables: & \multicolumn{2}{c}{high\_filing\_dest} & Avg real rent (destination building)\\
                                              & m4             & m5              & m\_rent \\    
      Model:                                  & (1)            & (2)             & (3)\\  
      \midrule
      \emph{Variables}\\
      high\_filing\_origTRUE                  & 0.0571$^{***}$ & 0.0698$^{***}$  &   \\   
                                              & (0.0052)       & (0.0140)        &   \\   
      Avg real rent (destination building)    &                & -0.0180$^{***}$ &   \\   
                                              &                & (0.0063)        &   \\   
      Avg real rent (origin building)         &                & -0.0033         & 0.2192$^{***}$\\   
                                              &                & (0.0044)        & (0.0072)\\   
      Filing rate (origin, raw long-run)      &                &                 & -0.0130$^{*}$\\   
                                              &                &                 & (0.0068)\\   
      Filing rate (destination, raw long-run) &                &                 & -0.2731$^{***}$\\   
                                              &                &                 & (0.0399)\\   
      \midrule
      \emph{Fixed-effects}\\
      Units bin (destination)                 & Yes            & Yes             & Yes\\  
      Units bin (origin)                      & Yes            & Yes             & Yes\\  
      Destination tract FE                    & Yes            & Yes             & Yes\\  
      Origin tract FE                         & Yes            & Yes             & Yes\\  
      \midrule
      \emph{Fit statistics}\\
      Observations                            & 87,976         & 20,209          & 56,412\\  
      \midrule \midrule
      \multicolumn{4}{l}{\emph{Clustered (pid) standard-errors in parentheses}}\\
      \multicolumn{4}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
   \end{tabular}

\end{adjustbox}
\end{table}

\subsection{Trajectory Filing Outcomes (Raw Long-Run Filing
Rate)}\label{trajectory-filing-outcomes-raw-long-run-filing-rate}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Change in filing rate (destination - origin, raw long-run)}\\
                                                  & Delta A        & Delta B      & Delta C         & Delta D \\   
   Model:                                         & (1)            & (2)          & (3)             & (4)\\  
   \midrule
   \emph{Variables}\\
   Constant                                       & 0.0027$^{***}$ &              &                 &   \\   
                                                  & (0.0005)       &              &                 &   \\   
   Middle building filing-rate bin $=$ [1,5)")    & -0.0039        & -0.0053      & 0.0006          & 0.0018\\   
                                                  & (0.0057)       & (0.0052)     & (0.0028)        & (0.0031)\\   
   Middle building filing-rate bin $=$ [5,10)")   & -0.0005        & 0.0009       & 0.0080$^{***}$  & 0.0067$^{***}$\\   
                                                  & (0.0017)       & (0.0019)     & (0.0017)        & (0.0015)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0008         & 0.0025       & 0.0164$^{***}$  & 0.0145$^{***}$\\   
                                                  & (0.0017)       & (0.0018)     & (0.0021)        & (0.0021)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0027         & 0.0048$^{*}$ & 0.0398$^{***}$  & 0.0309$^{***}$\\   
                                                  & (0.0029)       & (0.0028)     & (0.0044)        & (0.0031)\\   
   Origin filing rate (raw long-run)              &                &              & -0.9800$^{***}$ &   \\   
                                                  &                &              & (0.0158)        &   \\   
   Log(origin total area)                         &                &              & 0.0025$^{*}$    & -0.0011\\   
                                                  &                &              & (0.0013)        & (0.0020)\\   
   Log(origin market value)                       &                &              & -0.0040         & -0.0070$^{***}$\\   
                                                  &                &              & (0.0026)        & (0.0026)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                &                & Yes          & Yes             & \\  
   Origin year-built decade FE                    &                &              & Yes             & Yes\\  
   Origin unit-bin FE                             &                &              & Yes             & Yes\\  
   Origin building-type FE                        &                &              & Yes             & Yes\\  
   Origin quality-grade FE                        &                &              & Yes             & Yes\\  
   Origin stories-bin FE                          &                &              & Yes             & Yes\\  
   Origin tract x origin filing-bin FE            &                &              &                 & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,284        & 160,279      & 157,468         & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Destination filing rate (raw long-run)}\\
                                                  & Dest A         & Dest B         & Dest C         & Dest D \\   
   Model:                                         & (1)            & (2)            & (3)            & (4)\\  
   \midrule
   \emph{Variables}\\
   Middle building filing-rate bin $=$ [1,5)")    & 0.0039         & 0.0037         & 0.0006         & 0.0022\\   
                                                  & (0.0025)       & (0.0025)       & (0.0028)       & (0.0029)\\   
   Middle building filing-rate bin $=$ [5,10)")   & 0.0098$^{***}$ & 0.0096$^{***}$ & 0.0080$^{***}$ & 0.0076$^{***}$\\   
                                                  & (0.0018)       & (0.0019)       & (0.0017)       & (0.0015)\\   
   Middle building filing-rate bin $=$ [10,20)")  & 0.0188$^{***}$ & 0.0184$^{***}$ & 0.0164$^{***}$ & 0.0153$^{***}$\\   
                                                  & (0.0022)       & (0.0024)       & (0.0021)       & (0.0019)\\   
   Middle building filing-rate bin $=$ [20,inf)") & 0.0463$^{***}$ & 0.0452$^{***}$ & 0.0398$^{***}$ & 0.0365$^{***}$\\   
                                                  & (0.0049)       & (0.0054)       & (0.0044)       & (0.0038)\\   
   Origin filing rate (raw long-run)              &                & 0.0250         & 0.0200         &   \\   
                                                  &                & (0.0177)       & (0.0158)       &   \\   
   Log(origin total area)                         &                &                & 0.0025$^{*}$   & 0.0015\\   
                                                  &                &                & (0.0013)       & (0.0012)\\   
   Log(origin market value)                       &                &                & -0.0040        & -0.0038$^{*}$\\   
                                                  &                &                & (0.0026)       & (0.0022)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                & Yes            & Yes            & Yes            & \\  
   Origin year-built decade FE                    &                &                & Yes            & Yes\\  
   Origin unit-bin FE                             &                &                & Yes            & Yes\\  
   Origin building-type FE                        &                &                & Yes            & Yes\\  
   Origin quality-grade FE                        &                &                & Yes            & Yes\\  
   Origin stories-bin FE                          &                &                & Yes            & Yes\\  
   Origin tract x origin filing-bin FE            &                &                &                & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,279        & 160,279        & 157,468        & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccc}
   \tabularnewline \midrule \midrule
   Dependent Variable: & \multicolumn{4}{c}{Destination filing rate (raw long-run)}\\
                                                   & Dest A         & Dest B         & Dest C         & Dest D \\   
   Model:                                          & (1)            & (2)            & (3)            & (4)\\  
   \midrule
   \emph{Variables}\\
   Middle building high-filing indicator (>=15\%)  & 0.0349$^{***}$ & 0.0341$^{***}$ & 0.0305$^{***}$ & 0.0277$^{***}$\\   
                                                   & (0.0038)       & (0.0042)       & (0.0035)       & (0.0030)\\   
   Origin filing rate (raw long-run)               &                & 0.0262         & 0.0208         &   \\   
                                                   &                & (0.0180)       & (0.0161)       &   \\   
   Log(origin total area)                          &                &                & 0.0026$^{*}$   & 0.0016\\   
                                                   &                &                & (0.0013)       & (0.0012)\\   
   Log(origin market value)                        &                &                & -0.0043        & -0.0040$^{*}$\\   
                                                   &                &                & (0.0026)       & (0.0022)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                 & Yes            & Yes            & Yes            & \\  
   Origin year-built decade FE                     &                &                & Yes            & Yes\\  
   Origin unit-bin FE                              &                &                & Yes            & Yes\\  
   Origin building-type FE                         &                &                & Yes            & Yes\\  
   Origin quality-grade FE                         &                &                & Yes            & Yes\\  
   Origin stories-bin FE                           &                &                & Yes            & Yes\\  
   Origin tract x origin filing-bin FE             &                &                &                & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                    & 160,279        & 160,279        & 157,468        & 157,338\\  
   \midrule \midrule
   \multicolumn{5}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{5}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\subsection{LOO Tract Filing Rate Outcomes (Raw Appendix
Robustness)}\label{loo-tract-filing-rate-outcomes-raw-appendix-robustness}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccccc}
   \tabularnewline \midrule \midrule
   Dependent Variables: & \multicolumn{2}{c}{Change in LOO tract filing rate (raw)} & \multicolumn{4}{c}{Destination LOO tract filing rate (raw)}\\
                                                  & Delta A                & Delta B        & Dest A                & Dest B         & Dest C         & Dest D \\   
   Model:                                         & (1)                    & (2)            & (3)                   & (4)            & (5)            & (6)\\  
   \midrule
   \emph{Variables}\\
   Constant                                       & $-5.33\times 10^{-5}$  &                &                       &                &                &   \\   
                                                  & (0.0006)               &                &                       &                &                &   \\   
   Middle building filing-rate bin $=$ [1,5)")    & -0.0004                & 0.0002         & $2.54\times 10^{-5}$  & 0.0001         & 0.0003         & 0.0004\\   
                                                  & (0.0016)               & (0.0008)       & (0.0009)              & (0.0008)       & (0.0005)       & (0.0005)\\   
   Middle building filing-rate bin $=$ [5,10)")   & $-3.01\times 10^{-5}$  & 0.0003         & 0.0002                & 0.0003         & 0.0004         & 0.0004\\   
                                                  & (0.0002)               & (0.0003)       & (0.0003)              & (0.0003)       & (0.0002)       & (0.0002)\\   
   Middle building filing-rate bin $=$ [10,20)")  & $2.42\times 10^{-5}$   & 0.0006         & 0.0005                & 0.0006         & 0.0006         & 0.0006$^{*}$\\   
                                                  & (0.0003)               & (0.0004)       & (0.0005)              & (0.0004)       & (0.0004)       & (0.0004)\\   
   Middle building filing-rate bin $=$ [20,inf)") & $-9.52\times 10^{-5}$  & 0.0011$^{***}$ & 0.0006                & 0.0009$^{**}$  & 0.0011$^{***}$ & 0.0009$^{***}$\\   
                                                  & (0.0004)               & (0.0004)       & (0.0005)              & (0.0004)       & (0.0003)       & (0.0003)\\   
   Origin LOO tract filing rate (raw)             &                        &                &                       & 0.7790$^{***}$ & 0.8058$^{***}$ &   \\   
                                                  &                        &                &                       & (0.1025)       & (0.1230)       &   \\   
   Log(origin total area)                         &                        &                &                       &                & -0.0004        & -0.0005\\   
                                                  &                        &                &                       &                & (0.0005)       & (0.0004)\\   
   Log(origin market value)                       &                        &                &                       &                & -0.0004        & -0.0004\\   
                                                  &                        &                &                       &                & (0.0004)       & (0.0003)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                &                        & Yes            & Yes                   & Yes            & Yes            & \\  
   Origin year-built decade FE                    &                        &                &                       &                & Yes            & Yes\\  
   Origin unit-bin FE                             &                        &                &                       &                & Yes            & Yes\\  
   Origin building-type FE                        &                        &                &                       &                & Yes            & Yes\\  
   Origin quality-grade FE                        &                        &                &                       &                & Yes            & Yes\\  
   Origin stories-bin FE                          &                        &                &                       &                & Yes            & Yes\\  
   Origin tract x origin filing-bin FE            &                        &                &                       &                &                & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                   & 160,667                & 160,658        & 160,658               & 160,658        & 157,691        & 157,563\\  
   \midrule \midrule
   \multicolumn{7}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{7}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}

\begin{adjustbox}{max width=\textwidth}
\begingroup
\centering
\begin{tabular}{lcccccc}
   \tabularnewline \midrule \midrule
   Dependent Variables: & \multicolumn{2}{c}{Change in LOO tract filing rate (raw)} & \multicolumn{4}{c}{Destination LOO tract filing rate (raw)}\\
                                                   & Delta A                & Delta B  & Dest A   & Dest B         & Dest C         & Dest D \\   
   Model:                                          & (1)                    & (2)      & (3)      & (4)            & (5)            & (6)\\  
   \midrule
   \emph{Variables}\\
   Constant                                        & $-6.88\times 10^{-5}$  &          &          &                &                &   \\   
                                                   & (0.0006)               &          &          &                &                &   \\   
   Middle building high-filing indicator (>=15\%)  & -0.0002                & 0.0006   & 0.0003   & 0.0006         & 0.0007$^{**}$  & 0.0006$^{*}$\\   
                                                   & (0.0003)               & (0.0004) & (0.0005) & (0.0004)       & (0.0003)       & (0.0003)\\   
   Origin LOO tract filing rate (raw)              &                        &          &          & 0.7780$^{***}$ & 0.8049$^{***}$ &   \\   
                                                   &                        &          &          & (0.1033)       & (0.1233)       &   \\   
   Log(origin total area)                          &                        &          &          &                & -0.0004        & -0.0005\\   
                                                   &                        &          &          &                & (0.0005)       & (0.0004)\\   
   Log(origin market value)                        &                        &          &          &                & -0.0004        & -0.0004\\   
                                                   &                        &          &          &                & (0.0004)       & (0.0003)\\   
   \midrule
   \emph{Fixed-effects}\\
   Origin tract FE                                 &                        & Yes      & Yes      & Yes            & Yes            & \\  
   Origin year-built decade FE                     &                        &          &          &                & Yes            & Yes\\  
   Origin unit-bin FE                              &                        &          &          &                & Yes            & Yes\\  
   Origin building-type FE                         &                        &          &          &                & Yes            & Yes\\  
   Origin quality-grade FE                         &                        &          &          &                & Yes            & Yes\\  
   Origin stories-bin FE                           &                        &          &          &                & Yes            & Yes\\  
   Origin tract x origin filing-bin FE             &                        &          &          &                &                & Yes\\  
   \midrule
   \emph{Fit statistics}\\
   Observations                                    & 160,667                & 160,658  & 160,658  & 160,658        & 157,691        & 157,563\\  
   \midrule \midrule
   \multicolumn{7}{l}{\emph{Clustered (Origin block group) standard-errors in parentheses}}\\
   \multicolumn{7}{l}{\emph{Signif. Codes: ***: 0.01, **: 0.05, *: 0.1}}\\
\end{tabular}
\par\endgroup

\end{adjustbox}




\end{document}
