---
title: "Annual Comparative Statics: Racial Composition and Complaint Filing"
author: "Philly Evictions Project"
date: today
format:
  pdf:
    pdf-engine: xelatex
    documentclass: article
    geometry: margin=0.75in
    fontsize: 10pt
    keep-tex: true
    number-sections: true
    toc: true
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{adjustbox}
        \usepackage{pdflscape}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 300
)
```

# Overview

This writeup presents annual-frequency complaint regressions using `infousa_pct_black` as a proxy for building racial composition.
It addresses limitations of the quarterly analysis: InfoUSA demographics are annual, so quarterly/monthly repetition inflates apparent precision.
All models use **Poisson fixed-effects** (`fepois`) with `offset = log(total_units)` to model complaint **rates** per unit.
As of the retaliatory refactor, this is the canonical location for complaint-suppression evidence; those blocks were removed from `writeups/retaliatory-evictions.qmd`.

**Inputs:**

- `bldg_panel_blp` (PID $\times$ year): demographics, building observables, rent, filing rates
- `building_data` (annual): complaints, permits, violations

**Key design choices:**

- **Pre-COVID sample:** year range 2007--2019
- **Lagged race:** all specs use `pct_black_l1` (one-year lag) to address simultaneity
- Sample filter: `!is.na(infousa_pct_black)` only (not the stricter `tenant_comp_missing == 0`)
- Maintenance controls: L1--L3 lagged repair-permit flow rates per unit
- Severe violation controls: L1--L3 lagged hazardous + unsafe violation rates per unit
- Clustering: PID level throughout

```{r load-helpers}
suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
  library(kableExtra)
})
qmd_path <- knitr::current_input(dir = TRUE)
proj_root <- normalizePath(file.path(dirname(qmd_path), ".."), winslash = "/", mustWork = FALSE)
source(file.path(proj_root, "r", "config.R"))
old_wd <- getwd()
setwd(proj_root)
on.exit(setwd(old_wd), add = TRUE)
cfg <- read_config(file.path(proj_root, "config.yml"))
tab_dir <- normalizePath(file.path(proj_root, "output", "comp-statics-annual-race", "tables"), winslash = "/", mustWork = FALSE)
fig_dir <- normalizePath(file.path(proj_root, "output", "comp-statics-annual-race", "figs"), winslash = "/", mustWork = FALSE)

include_tex_table <- function(path, landscape = FALSE) {
  if (!file.exists(path)) { cat("Table not found:", path); return(invisible(NULL)) }
  lines <- readLines(path)
  txt <- paste(lines, collapse = "\n")
  has_float <- grepl("\\\\begin\\{table\\}", txt)
  if (landscape) cat("\\begin{landscape}\n")
  if (has_float) {
    is_float <- grepl("^\\s*\\\\begin\\{table\\}|^\\s*\\\\end\\{table\\}", lines)
    is_meta <- grepl("^\\s*\\\\caption|^\\s*\\\\label|^\\s*\\\\centering", lines)
    cap_lines <- trimws(lines[is_meta])
    inner <- lines[!is_float & !is_meta]
    cat("\\begin{table}[htbp]\n\\centering\n")
    cat(cap_lines, sep = "\n")
    cat("\n{\\footnotesize\n\\begin{adjustbox}{max width=\\linewidth}\n")
    cat(inner, sep = "\n")
    cat("\n\\end{adjustbox}\n}\n\\end{table}\n")
  } else {
    cat("{\\footnotesize\n\\begin{adjustbox}{max width=\\linewidth}\n")
    cat(lines, sep = "\n")
    cat("\n\\end{adjustbox}\n}\n")
  }
  if (landscape) cat("\\end{landscape}\n")
}

read_csv_safe <- function(path) {
  if (!file.exists(path)) return(data.table())
  fread(path)
}
```

# Variance Decomposition

How much of the variation in `pct_black` is between-building versus within-building over time?
If PID FE absorb nearly all variation, then within-building specs will have little identifying power.

```{r vardecomp-table}
vd <- read_csv_safe(file.path(tab_dir, "compstats_annual_variance_decomposition.csv"))
if (nrow(vd)) {
  vd_show <- vd[, .(
    Variable = variable,
    N = n_obs,
    PIDs = n_pid,
    `Overall SD` = round(overall_sd, 4),
    `Between-PID SD` = round(between_pid_sd, 4),
    `Within-PID SD` = round(within_pid_sd, 4),
    `R2 (PID FE)` = round(r2_pid, 4),
    `R2 (GEOID x Year)` = round(r2_geoid_year, 4),
    `R2 (PID + GEOID x Year)` = round(r2_pid_geoid_year, 4)
  )]
  kable(vd_show, booktabs = TRUE,
        caption = "Variance decomposition of demographic composition variables") |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9)
} else {
  cat("Variance decomposition table not available.")
}
```

**Interpretation:** If `R2 (PID FE)` is very high (e.g., $> 0.90$), then racial composition is essentially a building-level fixed characteristic, and within-building variation is limited.
The within-PID SD relative to overall SD indicates how much time-series variation is available for identification under PID FE.

# Complaint Regression Ladder

Nine specs in a single table, progressing from cross-sectional to within-building identification. All use `pct_black_l1` (lagged race). Maintenance and severe-violation controls use L1--L3 lagged flow rates per unit.

**Cross-sectional (full sample):**

- **Spec 1:** `pct_black_l1 | year + unit_bin_fine` --- raw association
- **Spec 2:** `pct_black_l1 + log_total_area | year + tract + bldg obs` --- building + neighborhood, no maint/severity
- **Spec 3:** Spec 2 + `maint L1--L3 + severity L1--L3` --- adds maintenance/severity lags

**Rent subsample:**

- **Spec 4:** `pct_black_l1 + log_total_area + filing_rate + log_med_rent | ...` --- rent + filing only
- **Spec 5:** Spec 3 RHS + `filing_rate + log_med_rent` --- all controls

**Within-building (PID + year FE):**

- **Spec 6:** `pct_black_l1 | PID + year` --- raw within-building
- **Spec 7:** `pct_black_l1 + maint L1--L3 + severity L1--L3 | PID + year` --- within-building + lags

**Within-building (PID + census_tract $\times$ year FE):**

- **Spec 8:** `pct_black_l1 | PID + tract^year` --- within-building + market-year shocks
- **Spec 9:** `pct_black_l1 + maint L1--L3 + severity L1--L3 | PID + tract^year` --- within-building + market-year + lags

`log_total_area` is dropped from PID FE specs (collinear with building FE). The key diagnostic: does the `pct_black_l1` coefficient survive PID FE and tract$\times$year absorbers?

```{r ladder-tex, results='asis'}
fe_tex <- file.path(tab_dir, "compstats_annual_fe_ladder_etable.tex")
if (file.exists(fe_tex)) {
  include_tex_table(fe_tex, landscape = TRUE)
} else {
  cat("Regression ladder TeX table not available.")
}
```

```{r ladder-coefs}
fe_coefs <- read_csv_safe(file.path(tab_dir, "compstats_annual_fe_ladder_coefficients.csv"))
if (nrow(fe_coefs)) {
  fe_key <- fe_coefs[term == "pct_black_l1", .(
    Model = model, Term = term,
    Estimate = round(estimate, 4),
    SE = round(std_error, 4),
    `p-value` = signif(p_value, 3)
  )]
  kable(fe_key, booktabs = TRUE,
        caption = "pct\\_black\\_l1 coefficient across specifications") |>
    kable_styling(latex_options = "hold_position")
}
```

# Coverage Diagnostics

```{r coverage-table}
cov <- read_csv_safe(file.path(tab_dir, "compstats_annual_coverage_diagnostics.csv"))
if (nrow(cov)) {
  cov_show <- cov[, .(
    Year = year,
    `N obs` = n_obs,
    `N PIDs` = n_pid,
    `pct_black` = round(share_pct_black_nonmiss, 3),
    `pct_female` = round(share_pct_female_nonmiss, 3),
    `log rent` = round(share_log_med_rent_nonmiss, 3),
    `log area` = round(share_log_total_area_nonmiss, 3),
    `Mean sev. comp.` = round(mean_total_severe_complaints, 4),
    `Mean units` = round(mean_total_units, 2)
  )]
  kable(cov_show, booktabs = TRUE,
        caption = "Year-by-year coverage: share of PID-years with non-missing values") |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9)
}
```

# Sample Balance

Are buildings with missing demographics systematically different from those with observed demographics?

```{r balance-table}
bal <- read_csv_safe(file.path(tab_dir, "compstats_annual_sample_balance.csv"))
if (nrow(bal)) {
  bal_show <- bal[, .(
    `Has demog` = fifelse(has_demog == 1L, "Yes", "No"),
    `N obs` = n_obs,
    `N PIDs` = n_pid,
    `Mean units` = round(mean_total_units, 2),
    `Mean complaints` = round(mean_total_complaints, 4),
    `Mean severe` = round(mean_total_severe_complaints, 4),
    `Mean filing rate` = round(mean_filing_rate_annual, 4),
    `Share apartment` = round(share_apartment, 3)
  )]
  kable(bal_show, booktabs = TRUE,
        caption = "Sample balance: buildings with vs.~without InfoUSA demographics") |>
    kable_styling(latex_options = "hold_position")
}
```

# QA Summary

```{r qa-txt, results='asis'}
qa_path <- file.path(tab_dir, "compstats_annual_qa.txt")
if (file.exists(qa_path)) {
  qa <- readLines(qa_path)
  cat("\\begin{verbatim}\n")
  cat(qa, sep = "\n")
  cat("\n\\end{verbatim}\n")
} else {
  cat("QA file not available.")
}
```
