---
title: "Filing Rate Decomposition and Back-Rent Analysis"
subtitle: "Philadelphia Evictions, 2011--2019"
date: today
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    geometry: margin=1in
    fontsize: 11pt
    colorlinks: true
    header-includes: |
      \usepackage{booktabs}
      \usepackage{longtable}
      \usepackage{array}
      \usepackage{multirow}
      \usepackage[normalem]{ulem}
      \usepackage{wrapfig}
      \usepackage{float}
      \usepackage{colortbl}
      \usepackage{pdflscape}
      \usepackage{tabu}
      \usepackage{threeparttable}
      \usepackage{threeparttablex}
      \usepackage{makecell}
      \usepackage{xcolor}
      \usepackage{adjustbox}
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(data.table)
library(ggplot2)
library(kableExtra)

fd <- here::here("output/filing_decomposition")
p_fd <- function(...) file.path(fd, ...)

# Include a pre-written .tex file (from fixest etable) verbatim
include_tex <- function(path) {
  cat(paste(readLines(path), collapse = "\n"), "\n")
}
```

# Overview

This report summarizes two analyses of the Philadelphia eviction record (2011--2019):

1. **Entity consolidation** (`build-ownership-panel.R`): A two-phase owner linkage pipeline mapping RTT transfers and OPA parcels to legal entities and conglomerates.

2. **Filing rate decomposition** (`analyze-filing-decomposition.R`):
   - *Part A*: What fraction of cross-sectional variation in building-level filing rates is attributable to building characteristics, neighborhood, tenant composition, and landlord type?
   - *Part B*: Do corporate or high-filing landlords file evictions with less accumulated back rent? Is the plaintiff (often a management company) different from the owner?

**Commercial case filter (Part B):** Commercial cases are identified by the defendant in position 1 of the party-names table, not by the self-reported `commercial` flag in the evictions data (which is unreliable). Counterclaim parties (e.g.\ a corporate landlord counter-sued by a tenant) are excluded from the defendant classification. This is produced by `impute-race-preflight.R` (`eviction_case_commercial` product).

**Sample restrictions (Part B):** non-commercial cases, `ongoing_rent` 300--6000, `total_rent` 300--15000, `months >= 1`, single-parcel PID match, 2011--2019.

---

# Part 0: Entity Consolidation

## Two-phase owner linkage

Phase 1 normalizes raw RTT grantee names (stripping entity suffixes, roman numerals, bank/trust fragments)
and groups exact-match normalized names into **entities**. Persons and trusts are grouped by *(name, PID)*
rather than name alone, preventing common names from forming spurious hubs.

Phase 2 uses a name+address self-join on OPA mailing data: corporations match on *(business\_short\_name, address)*
where `business_short_name` further strips functional descriptor words (PROPERTIES, MANAGEMENT, REALTY, etc.);
persons/trusts match on *(exact name, address)*. A registered-agent filter drops addresses linked to more than 300
distinct entities. Connected components of the resulting name+address graph form **conglomerates**.

Phase 3 adds one-shot RTT→OPA transitive edges (last RTT grantee vs.\ 2024 OPA owner for each PID),
subject to a name-similarity gate: corporations must share the same `business_short_name` (≥4 chars);
persons must share ≥1 token of ≥5 characters. This prevents government entities (City of Philadelphia,
PHA) from absorbing hundreds of unrelated parcels acquired by tax-exempt conveyances not captured in RTT.

```{r consolidation-table}
consol <- data.table(
  Stage = c(
    "Phase 1 entities (RTT exact-name match)",
    "OPA-only entity additions",
    "Total entities",
    "Registered-agent addresses dropped (>300 entities each)",
    "Entities entering mailing-address graph",
    "Conglomerates formed",
    "Multi-entity conglomerates",
    "Phase 1 entities merged by Phase 2",
    "Name lookup entries (all sources)"
  ),
  Count = c(
    "451,346", "262,935", "714,281",
    "44 (all SIMPLIFILE LC E-RECORDING variants)",
    "64,461", "49,651", "3,063", "4,464", "719,215"
  )
)
kbl(consol, booktabs = TRUE, linesep = "",
    caption = "Entity consolidation summary") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, font_size = 9) |>
  column_spec(1, width = "9cm") |>
  column_spec(2, width = "5cm")
```

## PID $\times$ year coverage

```{r coverage-table}
cov <- data.table(
  Metric = c(
    "PID x year panel rows",
    "RTT-sourced owner rows",
    "OPA-fallback owner rows",
    "Entity ID coverage",
    "Portfolio bin: 1 PID",
    "Portfolio bin: 2--4 PIDs",
    "Portfolio bin: 5--19 PIDs",
    "Portfolio bin: 20+ PIDs"
  ),
  Value = c(
    "14,015,256 (583,969 PIDs x 24 years)",
    "5,128,881 (36.6%)",
    "8,886,375 (63.4%)",
    "14,015,256 (100%)",
    "3,522,595 (43.9% of 2011-19 PID-yrs)",
    "981,376 (12.2%)",
    "425,827 (5.3%)",
    "325,923 (4.1%)"
  )
)
kbl(cov, booktabs = TRUE, linesep = "",
    caption = "PID x year ownership panel coverage") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, font_size = 9) |>
  column_spec(1, width = "6cm") |>
  column_spec(2, width = "7cm")
```

---

# Part A: Cross-Sectional Filing Rate Decomposition

**Sample:** ever-rental buildings in 2011--2019 with non-missing EB filing rate, zip, census tract, and `rental_share`. N reported in table below. No minimum unit count restriction --- if a building appears in eviction filings it is treated as a rental.

**Rental share correction:** The EB filing rate denominator includes all observed unit-years, but single-family homes are sometimes rented only intermittently, deflating their apparent filing rates. All models (M1 onward) include `rental_share` = fraction of sample years with an active rental license, correcting for this. Philadelphia Housing Authority (PHA) buildings are exempt from the City licensing requirement; their `rental_share` is imputed to 1 (always fully rented).

## A1: Descriptive means by owner type and portfolio

```{r desc-landlord}
desc <- fread(p_fd("filing_decomp_descriptives_by_landlord.csv"))

if (!"mean_units_owned" %in% names(desc))
  stop("Column 'mean_units_owned' missing from filing_decomp_descriptives_by_landlord.csv — re-run analyze-filing-decomposition.R")

fmt_units <- function(x) ifelse(is.na(x), "---", format(round(x), big.mark = ","))

desc_owner <- desc[group_var == "owner_type", .(
  Group       = paste0("Owner: ", group_val),
  N_pids      = format(n_pids, big.mark = ","),
  Mean_units  = fmt_units(mean_units_owned),
  Mean_rate   = round(mean_filing_rate, 3),
  Median_rate = round(median_filing_rate, 3)
)]

desc_port <- desc[group_var == "portfolio_bin", .(
  Group       = paste0("Entity: ", group_val, " prop."),
  N_pids      = format(n_pids, big.mark = ","),
  Mean_units  = fmt_units(mean_units_owned),
  Mean_rate   = round(mean_filing_rate, 3),
  Median_rate = round(median_filing_rate, 3)
)]

desc_port_cong <- desc[group_var == "portfolio_bin_conglomerate", .(
  Group       = paste0("Cong.: ", group_val, " prop."),
  N_pids      = format(n_pids, big.mark = ","),
  Mean_units  = fmt_units(mean_units_owned),
  Mean_rate   = round(mean_filing_rate, 3),
  Median_rate = round(median_filing_rate, 3)
)]

desc_show <- rbind(desc_owner, desc_port, desc_port_cong)

kbl_tbl <- kbl(desc_show, booktabs = TRUE, linesep = "",
    col.names = c("Group", "N (PIDs)", "Mean units owned", "Mean EB rate", "Median EB rate"),
    caption = "EB filing rate by owner type and portfolio (cross-section, 2011--2019). Mean units owned = avg total units across all properties in the landlord's portfolio.") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, font_size = 9) |>
  column_spec(1, width = "4.5cm") |>
  column_spec(3, width = "2.5cm") |>
  pack_rows("Owner type (Person = reference)", 1, nrow(desc_owner)) |>
  pack_rows("Entity portfolio (per LLC/name)",
            nrow(desc_owner) + 1, nrow(desc_owner) + nrow(desc_port))

if (nrow(desc_port_cong) == 0)
  stop("No 'portfolio_bin_conglomerate' rows in descriptives CSV — re-run analyze-filing-decomposition.R")

kbl_tbl <- kbl_tbl |>
  pack_rows("Conglomerate portfolio (all linked LLCs)",
            nrow(desc_owner) + nrow(desc_port) + 1, nrow(desc_show))

kbl_tbl
```

Nonprofits stand out with a mean EB rate of 0.18 --- far above the other types and likely reflecting a small set of high-density affordable-housing buildings with concentrated poverty. PHA-owned buildings also exceed person-owned buildings (0.10 vs.\ 0.05). For-profit corporations file at 0.07, modestly above the 0.05 person baseline.

## A2: Sequential $R^2$ Decomposition

Six nested OLS models, weighted by `total_units`, outcome =
`filing_rate_eb_pre_covid`. $\Delta R^2$ isolates the variance
attributable to each group of factors added. M4 and M5 both branch from M3:
M4 uses entity-level portfolio (per LLC/name); M5 uses conglomerate-level portfolio
(across all linked LLCs under common ownership, from improved Phase 2/3 reconciliation).
M5's $\Delta R^2$ is relative to M3.

```{r r2-decomp}
r2 <- fread(p_fd("filing_decomp_r2_decomposition.csv"))

r2_show <- r2[, .(
  Model       = model,
  Description = gsub("_", "\\_", description, fixed = TRUE),
  R2          = ifelse(is.na(r2),       "---", sprintf("%.4f", r2)),
  AdjR2       = ifelse(is.na(adj_r2),   "---", sprintf("%.4f", adj_r2)),
  DeltaR2     = ifelse(is.na(delta_r2), "---", sprintf("%.4f", delta_r2)),
  N           = ifelse(is.na(n),        "---", format(n, big.mark = ","))
)]

kbl(r2_show, booktabs = TRUE, linesep = "", escape = FALSE,
    col.names = c("Model", "Description",
                  "$R^2$", "Adj.\\ $R^2$", "$\\Delta R^2$", "N"),
    caption = paste0(
      "Sequential $R^2$ decomposition. Between-neighborhood raw variance share: ",
      round(r2$between_nhood_share_raw[1], 3), ".")) |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, font_size = 9) |>
  column_spec(2, width = "5.5cm") |>
  footnote(general = "Weighted by mean total units. Cluster SE at tract.",
           general_title = "Note:", footnote_as_chunk = TRUE)
```

**Interpretation.** Neighborhood (tract FE) contributes the dominant share of explained variance, roughly $9\times$ the landlord component. Tenant racial composition adds a further increment, suggesting neighborhood sorting by race is a distinct channel from simple geographic sorting. The `rental_share` covariate (included from M1) corrects for the deflated filing rates of intermittently-rented properties; its $\Delta R^2$ contribution is absorbed into M1 and is not separately isolated. The landlord-type effect is small but present; numbers updated after re-run.

```{r r2-plot}
#| fig-cap: "Incremental R-squared by component group. Outcome: EB filing rate. Weighted by unit count. Portfolio bars show delta from M3 for entity (M4) and conglomerate (M5) portfolio measures."
#| fig-height: 3.5

if (!"M5" %in% r2$model)
  stop("M5 model missing from filing_decomp_r2_decomposition.csv — re-run analyze-filing-decomposition.R")

r2_plot <- data.table(
  component = c("Building +\nZip chars", "Neighborhood\n(Tract FE)",
                "Tenant racial\ncomposition",
                "Landlord +\nEntity portfolio",
                "Landlord +\nCong. portfolio"),
  delta     = c(
    r2$r2[r2$model == "M1"],
    r2$delta_r2[r2$model == "M2"],
    r2$delta_r2[r2$model == "M3"],
    r2$delta_r2[r2$model == "M4"],
    r2$delta_r2[r2$model == "M5"]
  ),
  group = c("Building/Nhood", "Building/Nhood", "Tenant", "Portfolio", "Portfolio")
)
r2_plot[, component := factor(component, levels = component)]

ggplot(r2_plot, aes(x = component, y = delta, fill = group)) +
  geom_col(width = 0.55) +
  geom_text(aes(label = sprintf("%.3f", delta)), vjust = -0.5, size = 3) +
  scale_fill_manual(values = c(
    "Building/Nhood" = "#2c7bb6",
    "Tenant"         = "#d7191c",
    "Portfolio"      = "#1a9641"
  ), guide = "none") +
  labs(x = NULL, y = expression(Delta * R^2)) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.major.x = element_blank())
```

## A3: OLS Coefficient Table (M1--M5)

M4 and M5 show entity vs.\ conglomerate portfolio on comparable samples. Note that M5 uses a
separate sample from M1--M4 (see N row), so coefficient comparisons across M4/M5 are directional.

```{r xsec-etable, results='asis'}
include_tex(p_fd("filing_decomp_xsec_etable.tex"))
```

---

# Part B: Case-Level Back-Rent Analysis

## B0: Sample

```{r sample-stats}
sample_stats <- data.table(
  Step = c(
    "Eviction cases 2011--2019 (before commercial filter)",
    "Commercial cases dropped (defendant #1 is a business entity)",
    "Non-commercial cases retained",
    "After rent/months filters (ongoing > 0, months >= 1)",
    "After PID linkage (unique-parcel match)",
    "After rent winsorization (ongoing 300--6000, total 300--15000)",
    "Entity ID (building owner) linked",
    "Plaintiff in name lookup",
    "Plaintiff is building owner (exact entity match)",
    "--- Plaintiff type breakdown (winsorized sample) ---",
    "  For-profit corporate plaintiff",
    "  Philadelphia Housing Authority (PHA) plaintiff",
    "  Nonprofit / affordable-housing plaintiff",
    "  Individual plaintiff",
    "--- Owner type breakdown ---",
    "  Person owner",
    "  For-profit corp owner",
    "  PHA owner",
    "  Nonprofit owner"
  ),
  Value = c(
    "207,244", "5,669", "201,575",
    "163,644", "153,746 (76.3%)", "152,733",
    "95.5%", "29.1%", "15.8%",
    "",
    "51.5% (78,615)", "4.1% (6,317)", "2.3% (3,518)", "42.1% (64,283)",
    "",
    "48.1% (73,467)", "46.6% (71,186)", "3.6% (5,560)", "1.7% (2,520)"
  )
)
kbl(sample_stats, booktabs = TRUE, linesep = "",
    caption = "Case-level sample construction") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, font_size = 9) |>
  column_spec(1, width = "10cm") |>
  column_spec(2, width = "3cm")
```

Only 15.8\% of cases have a plaintiff matching the building owner entity exactly, confirming that management companies file the majority of evictions.

**Note on PHA plaintiff cases:** 6,317 PHA plaintiff cases survive the rent filter (4.1\% of the winsorized sample). PHA income-based rents have a median of \$221/month and roughly 78\% fall below the \$300 rent floor; the surviving cases represent above-poverty-line PHA tenants in higher-rent units.

**Note on PHA owner type:** 5,560 cases are in PHA-owned buildings (3.6\%). The PHA-owned flag uses entity-ID matching through the name-lookup table, so it identifies the subset of cases where the building is formally owned by the Housing Authority regardless of who filed.

## B1: Descriptive statistics

```{r backrent-desc}
bd <- fread(p_fd("backrent_descriptives_by_landlord.csv"))

get_bd <- function(dt, gvar, col, labels) {
  dt[group_var == gvar & !is.na(get(col)),
    .(Category = labels[as.character(get(col))],
      N        = format(n_cases, big.mark = ","),
      `Med. months`  = round(median_months, 2),
      `Mean rent`    = sprintf("$%.0f", mean_ongoing_rent),
      `Mean cong. units` = sprintf("%.0f", mean_total_units_conglomerate_yr),
      `Pct. win`     = sprintf("%.1f%%", 100 * pct_plaintiff_win))]
}

if (!"mean_total_units_conglomerate_yr" %in% names(bd))
  stop("Column 'mean_total_units_conglomerate_yr' missing from backrent_descriptives_by_landlord.csv — re-run analyze-filing-decomposition.R")

bd_show <- rbind(
  get_bd(bd, "is_forprofit_corp_plaintiff", "is_forprofit_corp_plaintiff",
         c("FALSE" = "Non-fp-corp plaintiff", "TRUE" = "For-profit corp plaintiff")),
  get_bd(bd, "is_pha_plaintiff", "is_pha_plaintiff",
         c("FALSE" = "Non-PHA plaintiff",     "TRUE" = "PHA plaintiff")),
  get_bd(bd, "is_nonprofit_plaintiff", "is_nonprofit_plaintiff",
         c("FALSE" = "Non-nonprofit plaint.", "TRUE" = "Nonprofit plaintiff")),
  get_bd(bd, "is_corp_owner",     "is_corp_owner",
         c("FALSE" = "Person owner",          "TRUE" = "Corporate owner")),
  get_bd(bd, "is_pha_owner",      "is_pha_owner",
         c("FALSE" = "Non-PHA owner",         "TRUE" = "PHA owner")),
  get_bd(bd, "plaintiff_is_owner","plaintiff_is_owner",
         c("FALSE" = "Mgmt co. filer",        "TRUE" = "Owner-filer")),
  get_bd(bd, "high_filer_bldg",   "high_filer_bldg",
         c("FALSE" = "Lower-filing bldg",     "TRUE" = "High-filing bldg"))
)

bd_scale <- bd[group_var == "total_units_conglomerate_yr_net_parcel_bin" &
                 !is.na(total_units_conglomerate_yr_net_parcel_bin),
  .(Category = paste0("Scale: ", total_units_conglomerate_yr_net_parcel_bin),
    N        = format(n_cases, big.mark = ","),
    `Med. months`  = round(median_months, 2),
    `Mean rent`    = sprintf("$%.0f", mean_ongoing_rent),
    `Mean cong. units` = sprintf("%.0f", mean_total_units_conglomerate_yr),
    `Pct. win`     = sprintf("%.1f%%", 100 * pct_plaintiff_win))]

if (nrow(bd_scale) == 0)
  stop("No 'total_units_conglomerate_yr_net_parcel_bin' rows in descriptives CSV — re-run analyze-filing-decomposition.R")

bd_show_all <- rbind(bd_show, bd_scale)

n_main <- nrow(bd_show)
n_all  <- nrow(bd_show_all)

kbl(bd_show_all, booktabs = TRUE, linesep = "",
    caption = "Back-rent descriptives by landlord/plaintiff type and landlord scale (winsorized sample). Mean cong.\\ units = mean total units across the conglomerate portfolio in the case year.") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, font_size = 9) |>
  column_spec(1, width = "4.5cm") |>
  pack_rows("By plaintiff/owner type", 1, n_main) |>
  pack_rows("By landlord scale (units outside this building)", n_main + 1, n_all)
```

## B2: Months-of-Arrears Regressions

Outcome: $\log(\text{months})$ of back rent at filing. Models use `plaintiff_type`
(Individual = reference) and `owner_type` (Person = reference) as categorical variables
rather than separate binary dummies, which keeps the reference group explicit and tests
all plaintiff/owner types jointly. All specs include year $\times$ tract fixed effects.
Specs B2--B4 add `total_units_conglomerate_yr_net_parcel_bin` --- a four-category
measure of the landlord's portfolio units in \emph{other} buildings (i.e.\ the conglomerate
total excluding the evicted parcel itself): single-property, small ($\leq$10 units),
medium (10--49 units), large (50$+$ units). This isolates scale effects from building-level
unit count already controlled by `num_units_bin`.
Specs B3--B4 further add building type and unit-size controls. Spec B5 is the back-rent
elasticity model with the same landlord scale control.
Standard errors clustered at the building (PID) level.

```{r months-etable, results='asis'}
include_tex(p_fd("backrent_months_etable.tex"))
```

**Key results:**

- **PHA plaintiff** files fastest: coefficient $\approx -0.41$ (B1) to $-0.48$ (B4),
  stable and large across all specifications. The effect is stronger than previously
  estimated, now that the sample includes single-unit rentals (PHA rarely evicts
  single-family tenants, sharpening the contrast).
- **Nonprofit plaintiff**: $\approx -0.14^{***}$ (B1), persisting at $\approx -0.10^{**}$
  in B3. Nonprofits enforce noticeably faster than individual landlords even after
  controlling for building type and neighborhood.
- **For-profit corporate plaintiff**: $\approx -0.09^{***}$ (B1), shrinking to
  $\approx -0.02^{*}$ ($p = 0.036$) in B3 with full controls. The effect is now
  statistically significant --- for-profit corporations file for modestly less arrears
  than individuals after conditioning on building characteristics and neighborhood.
- **Owner type** (Person = reference): For-profit corp and Nonprofit owners are
  indistinguishable from person owners ($p > 0.15$ in B3/B4). **PHA-owned buildings**
  have significantly *more* months of arrears at filing ($+0.09^{*}$, $p = 0.03$ in B3):
  tenants in PHA-owned buildings accumulate more debt before eviction is filed, consistent
  with PHA's more deliberate enforcement process.
- **High-filing buildings** evict sooner: main effect $-0.12$ (B3) to $-0.18$ (B4),
  highly significant throughout.
- **B4 interactions** (plaintiff type $\times$ high-filer building): All three corporate
  plaintiff types show significant positive interactions with the high-filer indicator
  (for-profit corp: $+0.085^{***}$; nonprofit: $+0.182^{***}$; PHA: $+0.326^{***}$).
  This means that in high-filer buildings, corporate and institutional plaintiffs file for
  *more* arrears relative to individual landlords in the same buildings --- the speed
  advantage of institutional filers is attenuated in buildings where eviction is already
  a routinized practice.
- **Plaintiff-is-owner** near zero throughout ($p > 0.3$), consistent with management
  companies acting as agents rather than behaving differently from owner-filers.

## B3: Back-Rent Elasticity

Outcome: $\log(\text{total rent})$. Tests whether the back-rent amount scales proportionally
with monthly rent ($\hat{\beta} = 1$) and how landlord type shifts the relationship.

```{r rent-etable, results='asis'}
include_tex(p_fd("backrent_rent_etable.tex"))
```

The `log(ongoing rent)` elasticity is approximately **0.71** (significantly below 1 at
any conventional level). This means higher-rent units are filed for proportionally
*less* total back rent --- consistent with landlords filing sooner at higher rent levels,
possibly because vacancy and legal costs loom larger relative to each month of arrears.
Among plaintiff types, only PHA shows a significant total-rent discount ($-0.32^{***}$),
partly mechanical because surviving PHA cases are already above the \$300 rent floor
and PHA policy triggers filing after one missed payment.

---

# Summary

```{r summary-table}
summ <- data.table(
  Finding = c(
    "Neighborhood sorting is the dominant source of filing rate variation",
    "Landlord type (owner type + entity portfolio) explains $\\approx$0.9\\% of cross-sectional variation",
    "Conglomerate portfolio (M5) explains similar share to entity portfolio (M4)",
    "PHA files fastest: 41--48\\% fewer log-months, highly stable across all specs",
    "Nonprofits file faster; for-profit corp effect significant with full controls",
    "High-filing buildings evict sooner; corporate types partially offset this in high-filer bldgs",
    "PHA-owned buildings accumulate more arrears before filing ($+$0.09$^{*}$)",
    "Back-rent elasticity w.r.t.\\ monthly rent = 0.71 (significantly below 1.0)",
    "Plaintiff = building owner in only 15.8\\% of cases"
  ),
  Evidence = c(
    "$\\Delta R^2$(tract FE) $\\approx$ 0.082 vs.\\ $\\Delta R^2$(landlord) $\\approx$ 0.009",
    "M4 incremental $R^2$ from M3; robust to PPML",
    "M5 $\\Delta R^2$ from M3 comparable to M4; conglomerate portfolio in B5 reg.",
    "B1: $-0.41^{***}$; B4: $-0.48^{***}$; 6,317 cases survive \\$300 rent floor",
    "Nonprofit B3: $-0.10^{**}$; for-profit corp B3: $-0.02^{*}$, $p = 0.036$",
    "B4 interaction for-profit$\\times$high-filer: $+0.085^{***}$; nonprofit: $+0.182^{***}$",
    "B3 owner\\_typePHA: $+0.090^{*}$, $p = 0.030$",
    "Elasticity $\\approx$ 0.71; 95\\% CI excludes 1.0",
    "Name lookup exact match: 29.1\\%; entity match: 15.8\\%"
  )
)
kbl(summ, booktabs = TRUE, linesep = "", escape = FALSE,
    caption = "Key findings summary") |>
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, font_size = 9) |>
  column_spec(1, width = "7.5cm") |>
  column_spec(2, width = "6cm")
```

## Caveats

1. **Plaintiff lookup rate (29.1\%):** Most eviction plaintiffs are management companies
   not present in RTT or OPA by exact name. Fuzzy-name matching (Phase 3, deferred)
   could substantially improve coverage.

2. **OPA fallback ownership (63.4\% of PID-years):** Buildings with no RTT history
   inherit their 2024 OPA owner for all years, introducing attenuation bias if
   ownership changed during 2011--2019.

3. **Improved entity reconciliation (Phase 2/3):** As of the 2026-03-10 pipeline update,
   persons and trusts are grouped by (name, PID) rather than name alone. Phase 2 now
   uses name+address matching (not pure address sharing) to prevent registered-agent
   and government-hub explosion. Phase 3 adds a name-similarity gate preventing
   tax-exempt government conveyances from polluting private landlord conglomerates.
   These improvements make `portfolio_bin_conglomerate_yr` (M5/B5) a more reliable
   measure of true landlord scale than entity-level portfolio (M4).

4. **Racial disparity specs (B4):** Skipped --- defendant race imputation
   (`race_imputed_case_sample`) not yet available for this run.
