---
title: "Outer Sorting Baseline Simulation Memo"
author: "Philly Evictions Project"
date: today
format:
  pdf:
    pdf-engine: xelatex
    documentclass: article
    geometry: margin=1in
    fontsize: 11pt
    keep-tex: true
    number-sections: true
    toc: true
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{adjustbox}
        \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 9,
  fig.height = 6,
  dpi = 300
)
```

```{r load, include=FALSE}
suppressPackageStartupMessages({
  library(data.table)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
  library(patchwork)
})

resolve_proj_root <- function() {
  candidates <- c(getwd(), ".", "..", "../..")
  for (cand in candidates) {
    cfg_path <- file.path(cand, "config.yml")
    r_cfg_path <- file.path(cand, "r", "config.R")
    if (file.exists(cfg_path) && file.exists(r_cfg_path)) {
      return(normalizePath(cand, winslash = "/", mustWork = TRUE))
    }
  }
  stop("Could not locate project root from the Quarto render working directory.")
}

proj_root <- resolve_proj_root()
source(file.path(proj_root, "r", "config.R"))
source(file.path(proj_root, "r", "build-renter-poverty-geo.R"))
source(file.path(proj_root, "r", "build-outer-sorting-empirical-moments.R"))

old_wd <- getwd()
setwd(proj_root)
on.exit(setwd(old_wd), add = TRUE)

cfg <- read_config(file.path(proj_root, "config.yml"))
cfg_raw <- yaml::read_yaml(file.path(proj_root, "config.yml"))
cfg$paths$repo_root <- proj_root
cfg$paths$input_dir <- normalizePath(
  file.path(proj_root, cfg_raw$paths$input_dir %||% "data/input"),
  winslash = "/",
  mustWork = FALSE
)
cfg$paths$processed_dir <- normalizePath(
  file.path(proj_root, cfg_raw$paths$processed_dir %||% "data/processed"),
  winslash = "/",
  mustWork = FALSE
)
cfg$paths$output_dir <- normalizePath(
  file.path(proj_root, cfg_raw$paths$output_dir %||% "output"),
  winslash = "/",
  mustWork = FALSE
)
cfg$paths$tmp_dir <- normalizePath(
  file.path(proj_root, cfg_raw$paths$tmp_dir %||% "tmp"),
  winslash = "/",
  mustWork = FALSE
)

panel_path <- p_product(cfg, "outer_sorting_sim_panel")
moments_path <- p_product(cfg, "outer_sorting_sim_moments")
diagnostics_path <- p_product(cfg, "outer_sorting_sim_diagnostics")
calib_dir <- p_out(cfg, "outer_sorting")

panel <- fread(panel_path)
mom <- fread(moments_path)
diag <- fread(diagnostics_path)
best_params <- fread(file.path(calib_dir, "outer_sorting_calibration_best_params.csv"))
moment_compare <- fread(file.path(calib_dir, "outer_sorting_calibration_moment_comparison.csv"))
opt_summary <- fread(file.path(calib_dir, "outer_sorting_calibration_optimization_summary.csv"))
emp_built <- build_outer_sorting_empirical_panel(cfg)
emp_panel <- emp_built$panel

tab_dir <- file.path(calib_dir, "tables")
dir.create(tab_dir, recursive = TRUE, showWarnings = FALSE)

include_tex_table <- function(path, max_width = "\\textwidth") {
  if (!file.exists(path)) {
    cat("Table not found:", path)
    return(invisible(NULL))
  }
  lines <- readLines(path)
  if (identical(max_width, "\\tiny")) {
    begin_idx <- grep("^\\\\begin\\{table\\}", lines)
    if (length(begin_idx) >= 1L) {
      lines <- append(lines, values = "\\tiny", after = begin_idx[1])
    } else {
      lines <- c("{\\tiny", lines, "}")
    }
  }
  cat(lines, sep = "\n")
  cat("\n")
}

write_table_bundle <- function(dt, stem, caption, digits = 3) {
  csv_path <- file.path(tab_dir, paste0(stem, ".csv"))
  tex_path <- file.path(tab_dir, paste0(stem, ".tex"))
  fwrite(dt, csv_path)
  tex_lines <- capture.output(
    knitr::kable(
      dt,
      format = "latex",
      booktabs = TRUE,
      caption = caption,
      digits = digits,
      linesep = ""
    )
  )
  tex_lines <- sub("\\\\caption\\{\\\\label\\{tab:load\\}", "\\\\caption{", tex_lines)
  writeLines(tex_lines, tex_path)
  invisible(list(csv = csv_path, tex = tex_path))
}

outer_cfg <- cfg$run$outer_sorting
mu <- as.numeric(outer_cfg$mu)
delta_L <- as.numeric(outer_cfg$delta_L)
delta_H <- as.numeric(outer_cfg$delta_H)
avg_default <- (1 - mu) * delta_L + mu * delta_H

emp_units_year_from <- as.integer(outer_cfg$units_empirical_year_from %||% outer_cfg$empirical$year_from %||% 2011L)
emp_units_year_to <- as.integer(outer_cfg$units_empirical_year_to %||% outer_cfg$empirical$year_to %||% 2019L)
emp_units_year_built_col <- as.character(outer_cfg$units_empirical_year_built_col %||% outer_cfg$empirical$year_built_col %||% "year_built")
emp_units_path <- p_product(cfg, outer_cfg$units_empirical_product_key %||% outer_cfg$empirical$bldg_panel_product_key %||% "bldg_panel_blp")
emp_units_dt <- fread(emp_units_path, select = c("PID", "year", "total_units", emp_units_year_built_col))
setnames(emp_units_dt, emp_units_year_built_col, "year_built")
emp_units_dt[, year_built := suppressWarnings(as.integer(year_built))]
emp_units_dt <- emp_units_dt[
  year >= emp_units_year_from &
    year <= emp_units_year_to &
    (is.na(year_built) | year_built <= emp_units_year_to) &
    is.finite(total_units) &
    total_units > 0
]
emp_units_pid <- emp_units_dt[, .(
  observed_years = uniqueN(year),
  units_unit_years = sum(total_units, na.rm = TRUE)
), by = PID]
emp_units_pid <- emp_units_pid[observed_years > 0]
emp_units_pid[, avg_units := units_unit_years / observed_years]

unit_draw_summary <- data.table(
  sample = c("Empirical PID average annual units", "Simulated buildings"),
  n = c(nrow(emp_units_pid), nrow(panel)),
  mean_units = c(mean(emp_units_pid$avg_units), mean(panel$units)),
  p50_units = c(stats::quantile(emp_units_pid$avg_units, 0.50), stats::quantile(panel$units, 0.50)),
  p90_units = c(stats::quantile(emp_units_pid$avg_units, 0.90), stats::quantile(panel$units, 0.90)),
  p95_units = c(stats::quantile(emp_units_pid$avg_units, 0.95), stats::quantile(panel$units, 0.95)),
  p99_units = c(stats::quantile(emp_units_pid$avg_units, 0.99), stats::quantile(panel$units, 0.99)),
  max_units = c(max(emp_units_pid$avg_units), max(panel$units))
)

param_table <- data.table(
  block = c(
    "Simulation", "Simulation", "Simulation",
    "Tenant-side anchors", "Tenant-side anchors", "Tenant-side anchors",
    "Built environment", "Built environment",
    "Building age", "Building age",
    "Sorting", "Sorting",
    "Filing", "Filing", "Filing",
    "Complaints", "Complaints", "Complaints", "Complaints", "Complaints", "Complaints",
    "Maintenance", "Maintenance", "Maintenance", "Maintenance", "Maintenance",
    "Numerics", "Numerics", "Numerics", "Numerics"
  ),
  parameter = c(
    "B", "sim_year_from", "sim_year_to",
    "mu", "delta_L", "delta_H",
    "p_bad_shape1", "p_bad_shape2",
    "old_bldg_cutoff_year", "new_bldg_cutoff_year",
    "Dalph", "sigma_eta_sort",
    "aF", "bF_theta", "bF_delta",
    "aC", "bC_theta", "bC_s_bad", "bC_old", "bC_new", "bC_M",
    "m0", "bM_theta", "bM_old", "bM_new", "bM_C",
    "lam", "tol", "max_iter", "high_filing_threshold"
  ),
  value = c(
    outer_cfg$B, outer_cfg$sim_year_from, outer_cfg$sim_year_to,
    outer_cfg$mu, outer_cfg$delta_L, outer_cfg$delta_H,
    outer_cfg$p_bad_shape1, outer_cfg$p_bad_shape2,
    outer_cfg$old_bldg_cutoff_year, outer_cfg$new_bldg_cutoff_year,
    outer_cfg$Dalph, outer_cfg$sigma_eta_sort,
    outer_cfg$aF, outer_cfg$bF_theta, outer_cfg$bF_delta,
    outer_cfg$aC, outer_cfg$bC_theta, outer_cfg$bC_s_bad, outer_cfg$bC_old, outer_cfg$bC_new, outer_cfg$bC_M,
    outer_cfg$m0, outer_cfg$bM_theta, outer_cfg$bM_old, outer_cfg$bM_new, outer_cfg$bM_C,
    outer_cfg$lam, outer_cfg$tol, outer_cfg$max_iter, outer_cfg$high_filing_threshold
  ),
  status = c(
    "Fixed", "Fixed", "Fixed",
    "Fixed", "Fixed", "Fixed",
    "Calibrated", "Calibrated",
    "Fixed", "Fixed",
    "Calibrated", "Calibrated",
    "Calibrated", "Calibrated", "Calibrated",
    "Calibrated", "Calibrated", "Calibrated", "Calibrated", "Calibrated", "Calibrated",
    "Calibrated", "Calibrated", "Calibrated", "Calibrated", "Calibrated",
    "Calibrated", "Calibrated", "Calibrated",
    "Numeric", "Numeric", "Numeric", "Fixed"
  ),
  note = c(
    "Number of simulated buildings in the baseline run.",
    "First year in the simulation window used to annualize simulated outcomes.",
    "Last year in the simulation window used to annualize simulated outcomes.",
    "Citywide high-risk / precarious tenant share.",
    "Anchored low-risk default probability.",
    "Anchored high-risk default probability.",
    "Beta shape parameter for tract bad-type prevalence.",
    "Beta shape parameter for tract bad-type prevalence.",
    "Observed-building threshold for old-building indicator.",
    "Observed-building threshold for new-building indicator.",
    "Sorting strength in the logistic update.",
    "Neighborhood sorting shifter standard deviation.",
    "Filing log-rate intercept.",
    "Bad-type filing shift.",
    "Sensitivity of filings to average tenant default risk.",
    "Complaint intercept.",
    "Bad-type complaint shift.",
    "Complaint-composition slope for bad landlords only.",
    "Complaint shift for older buildings.",
    "Complaint shift for newer buildings.",
    "Complaint response to maintenance.",
    "Baseline per-unit maintenance rate.",
    "Bad-type maintenance shift.",
    "Maintenance shift for older buildings.",
    "Maintenance shift for newer buildings.",
    "Maintenance response to complaint intensity.",
    "Damping parameter in the fixed-point iteration.",
    "Stopping tolerance on the composition update.",
    "Maximum fixed-point iterations.",
    "Absolute filing-rate cutoff for high-filing moments."
  )
)

convergence_table <- data.table(
  metric = c(
    "Converged", "Iterations", "Max composition change",
    "Mass residual before final projection", "Mass residual after final projection",
    "Final xi", "Target mu", "Weighted mean s"
  ),
  value = c(
    as.character(diag$converged[1]),
    as.character(diag$iters[1]),
    format(diag$max_diff[1], scientific = TRUE, digits = 3),
    format(diag$mass_resid_before_final_proj[1], scientific = TRUE, digits = 3),
    format(diag$mass_resid_final[1], scientific = TRUE, digits = 3),
    sprintf("%.4f", diag$xi_final[1]),
    sprintf("%.3f", diag$mu_target[1]),
    sprintf("%.3f", diag$s_weighted_mean[1])
  )
)

eq_summary <- data.table(
  moment = c(
    "Mean filing rate", "Mean maintenance rate", "Mean complaint rate",
    "Zero filings share", "Zero maintenance share", "Zero complaints share",
    "Sorting slope on high filing within neighborhood",
    "Sorting slope: top filing bin vs low filing bin",
    "Complaint on composition",
    "Complaint on composition x high filing",
    "Maintenance on complaint intensity",
    "Residual SD of filing rate after neighborhood FE"
  ),
  value = c(
    mom$mean_f_rate[1],
    mom$mean_m_rate[1],
    mom$mean_c_rate[1],
    mom$zero_share_f[1],
    mom$zero_share_m[1],
    mom$zero_share_c[1],
    mom$sorting_coef_high_filing_nhood[1],
    mom$sorting_coef_high_bin_nhood[1],
    mom$beta_ppml_s[1],
    mom$beta_ppml_s_x_high_filing[1],
    mom$beta_maint_on_c_rate[1],
    mom$filing_resid_sd_nhood_fe[1]
  )
)

theta_summary <- panel[, .(
  mean_s = weighted.mean(s, units),
  mean_f_rate = weighted.mean(f_rate, units),
  mean_c_rate = weighted.mean(c_rate, units),
  mean_m_rate = weighted.mean(m_rate, units),
  zero_f = mean(F == 0L),
  zero_c = mean(C == 0L),
  zero_m = mean(M == 0L)
), by = theta]

nhood_summary <- panel[, .(
  mean_s = weighted.mean(s, units),
  mean_f_rate = weighted.mean(f_rate, units),
  mean_theta_bad = weighted.mean(theta_bad, units),
  total_units = sum(units),
  n_buildings = .N
), by = nhood]
nhood_summary[, size_bin := cut(
  total_units,
  breaks = unique(quantile(total_units, probs = seq(0, 1, 0.25), na.rm = TRUE)),
  include.lowest = TRUE,
  ordered_result = TRUE
)]

emp_nhood_summary <- emp_panel[, .(
  mean_s = weighted.mean(s, units),
  mean_f_rate = weighted.mean(f_rate, units),
  total_units = sum(units),
  n_buildings = .N
), by = nhood]

empirical_rate_check <- data.table(
  sample = c("Empirical target panel", "Empirical target panel"),
  statistic = c("mean_f_rate (unit-weighted)", "mean_f_rate (unweighted)"),
  value = c(
    weighted.mean(emp_panel$f_rate, emp_panel$units),
    mean(emp_panel$f_rate)
  )
)

nhood_dist_summary <- rbindlist(list(
  data.table(
    sample = "Empirical neighborhoods",
    metric = c("Neighborhood mean filing rate", "Neighborhood mean low-income share"),
    mean = c(mean(emp_nhood_summary$mean_f_rate), mean(emp_nhood_summary$mean_s)),
    p50 = c(stats::quantile(emp_nhood_summary$mean_f_rate, 0.50), stats::quantile(emp_nhood_summary$mean_s, 0.50)),
    p90 = c(stats::quantile(emp_nhood_summary$mean_f_rate, 0.90), stats::quantile(emp_nhood_summary$mean_s, 0.90))
  ),
  data.table(
    sample = "Simulated neighborhoods",
    metric = c("Neighborhood mean filing rate", "Neighborhood mean low-income share"),
    mean = c(mean(nhood_summary$mean_f_rate), mean(nhood_summary$mean_s)),
    p50 = c(stats::quantile(nhood_summary$mean_f_rate, 0.50), stats::quantile(nhood_summary$mean_s, 0.50)),
    p90 = c(stats::quantile(nhood_summary$mean_f_rate, 0.90), stats::quantile(nhood_summary$mean_s, 0.90))
  )
))

moment_compare_show <- moment_compare[, .(
  moment,
  target = round(target, 4),
  simulated = round(simulated, 4),
  weight,
  diff = signif(diff, 3)
)]

calibrated_compare <- best_params[
  calibrated == TRUE & param %chin% names(outer_cfg),
  .(
    parameter = param,
    baseline = as.numeric(unlist(outer_cfg[param])),
    calibrated = value,
    change = value - as.numeric(unlist(outer_cfg[param]))
  )
]

calibration_run_table <- data.table(
  metric = c("Target product", "Convergence code", "Objective", "Evaluations"),
  value = c(
    cfg$run$outer_sorting$calibration$target_product_key,
    as.character(opt_summary$convergence_code[1]),
    sprintf("%.4f", opt_summary$objective_best[1]),
    as.character(opt_summary$n_evaluations[1])
  )
)

top_miss_table <- moment_compare[order(-weighted_sq_error)][
  1:min(.N, 8L),
  .(
    moment,
    target = round(target, 4),
    simulated = round(simulated, 4),
    diff = round(diff, 4),
    weighted_sq_error = round(weighted_sq_error, 4)
  )
]

write_table_bundle(param_table, "outer_sorting_baseline_parameters", "Baseline outer sorting parameters", digits = 4)
write_table_bundle(convergence_table, "outer_sorting_convergence_summary", "Fixed-point convergence summary", digits = 4)
write_table_bundle(eq_summary, "outer_sorting_equilibrium_summary", "Equilibrium summary moments", digits = 4)
write_table_bundle(theta_summary, "outer_sorting_type_summary", "Equilibrium summary by landlord type", digits = 4)
write_table_bundle(moment_compare_show, "outer_sorting_moment_comparison_compact", "Calibration target vs simulated moments", digits = 4)
write_table_bundle(calibration_run_table, "outer_sorting_calibration_run_summary", "Calibration run summary", digits = 4)
write_table_bundle(calibrated_compare, "outer_sorting_calibrated_parameter_changes", "Baseline vs calibrated parameters", digits = 4)
write_table_bundle(top_miss_table, "outer_sorting_top_moment_misses", "Largest calibration moment misses", digits = 4)
write_table_bundle(unit_draw_summary, "outer_sorting_unit_draw_summary", "Empirical vs simulated unit distribution summary", digits = 4)
write_table_bundle(empirical_rate_check, "outer_sorting_empirical_rate_check", "Empirical filing-rate check", digits = 4)
write_table_bundle(nhood_dist_summary, "outer_sorting_nhood_distribution_summary", "Empirical vs simulated neighborhood distribution summary", digits = 4)
```

# Overview

This memo summarizes the baseline outer sorting simulation currently implemented in `r/simulate-outer-sorting.R` and the associated first-pass calibration setup in `r/calibrate-outer-sorting.R`.

The baseline normalization is:

$$
\bar\delta_b = s_b\delta_H + (1 - s_b)\delta_L,
\qquad
\bar f_b = \exp\!\left(a_F + b_{F\theta}\mathbf{1}\{\theta_b = B\} + b_{F\delta}\bar\delta_b\right),
\qquad
x_b \equiv \bar f_b,
\qquad
s_b^\star(\xi) = \Lambda(\xi + \Delta \alpha \bar f_b + \eta_{n(b)}).
$$

The filing block maps building composition into expected filings through average tenant default risk using a single log-rate equation. The complaint-composition channel is restricted to bad landlords, and maintenance is parameterized directly in per-unit levels through `m0`. The sorting signal is still the expected filing rate, and the simulation iterates on expected maintenance, complaint, and filing rates until the building composition vector is a fixed point under the citywide mass constraint.

# Simulation Setup

The baseline parameterization fixes the citywide high-risk share at $\mu = `r sprintf("%.2f", mu)`$, interpretable as a rough renter-poverty / precarious-tenant share. The tenant default anchors are set to $\delta_L = `r sprintf("%.2f", delta_L)`$ and $\delta_H = `r sprintf("%.2f", delta_H)`$, implying an average anchored default probability of roughly `r sprintf("%.3f", avg_default)`.

The baseline filing block uses average default risk, $\bar\delta_b = s_b\delta_H + (1-s_b)\delta_L$, inside a single log-rate Poisson structure. Complaints depend on composition only through the interaction `s_b × 1{\theta_b = B}`, reflecting the current theoretical restriction that complaint suppression operates only for bad landlords. The maintenance block is parameterized with `m0`, the baseline expected maintenance rate per unit. Both the maintenance and complaint equations now also include exogenous old-building and new-building indicators derived from empirically resampled `year_built`, so age-related upkeep differences do not have to be absorbed entirely by landlord type or complaint-response coefficients. The sorting block still includes a neighborhood shifter $\eta_{n(b)}$, so the model does not need to push all low-income-share dispersion through the filing process. On the empirical side, the current composition proxy is a building-level InfoUSA low-income share based on `find_div_1000` and a fixed income threshold. Simulated building units and year-built observables are drawn jointly by empirical resampling from the observed PID-level BLP distribution over `r emp_units_year_from`-`r emp_units_year_to`, rather than from the old stylized unit bins.

The realized simulation panel is now annualized over the configured simulation window rather than being a one-shot annual draw. For each simulated building, the code computes active exposure years from `year_built`, draws total counts over those unit-years from stationary Poisson processes, and divides back by exposure years. That makes the simulated `M`, `C`, `F`, `m_rate`, `c_rate`, and `f_rate` directly comparable to the empirical PID-level annualized objects built from `2011`-`2019`.

One implementation detail is worth being explicit about: after the final exact citywide-mass projection of `s`, the simulator refreshes the expected maintenance, complaint, and filing rates once at that projected composition rather than fully re-solving the maintenance/complaint subsystem conditional on the projected `s`. Under the current tight tolerances, this should be a small numerical approximation rather than a material change in the reported equilibrium.

```{r parameter-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_baseline_parameters.tex"), max_width = "\\tiny")
```

## Unit Exposure

```{r unit-draw-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_unit_draw_summary.tex"))
```

## Empirical Filing-Rate Check

```{r empirical-rate-check-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_empirical_rate_check.tex"), max_width = "0.65\\textwidth")
```

Under the current empirical target construction, the filing-rate target is about `r sprintf("%.3f", weighted.mean(emp_panel$f_rate, emp_panel$units))` on a unit-weighted basis and `r sprintf("%.3f", mean(emp_panel$f_rate))` on an unweighted building basis. If the intended raw-data benchmark is closer to `0.06`, that likely reflects a definitional difference in the empirical target rather than a calibration problem by itself.

# Convergence

The deterministic fixed-point algorithm converged cleanly in the current baseline run. The maximum change in the composition vector was below the configured tolerance, and the final citywide mass residual was effectively zero.

```{r convergence-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_convergence_summary.tex"), max_width = "0.75\\textwidth")
```

The simulation is solving the stationary equilibrium under the exact citywide mass constraint, so the weighted mean of simulated composition lines up with the target $\mu$ by construction.

# Resulting Equilibrium

The baseline equilibrium implies:

- unit-weighted mean filing, maintenance, and complaint rates of about `r sprintf("%.3f", mom$mean_f_rate[1])`, `r sprintf("%.3f", mom$mean_m_rate[1])`, and `r sprintf("%.3f", mom$mean_c_rate[1])` per unit
- substantial zero mass in the annualized outcomes, where zero shares are unweighted shares of buildings
- higher group-1 shares and higher filing / complaint intensity in bad-type buildings than in good-type buildings

```{r equilibrium-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_equilibrium_summary.tex"))
```

## By Landlord Type

```{r type-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_type_summary.tex"))
```

## Outcome Distributions

```{r rate-histograms, fig.cap="Distribution of realized filing, complaint, and maintenance rates across simulated buildings.", fig.align='center', out.width='95%'}
plot_dt <- melt(
  panel[, .(f_rate, c_rate, m_rate)],
  measure.vars = c("f_rate", "c_rate", "m_rate"),
  variable.name = "rate_type",
  value.name = "rate"
)
plot_dt[, rate_type := factor(rate_type, levels = c("f_rate", "c_rate", "m_rate"),
                              labels = c("Filing rate", "Complaint rate", "Maintenance rate"))]

ggplot(plot_dt, aes(x = rate)) +
  geom_density(fill = "#28536B", alpha = 0.70, color = NA, adjust = 1.1) +
  facet_wrap(~rate_type, scales = "free_x") +
  labs(x = "Rate", y = "Density") +
  coord_cartesian(xlim = c(0, 0.75)) +
  theme_minimal(base_size = 11)
```

```{r empirical-vs-sim-rate-histograms, fig.cap="Empirical vs simulated building-level distributions of filing and complaint rates per unit.", fig.align='center', out.width='95%', fig.width=10, fig.height=7}
compare_rate_dt <- rbindlist(list(
  data.table(source = "Empirical", metric = "Filing rate per unit", value = emp_panel$f_rate),
  data.table(source = "Simulated", metric = "Filing rate per unit", value = panel$f_rate),
  data.table(source = "Empirical", metric = "Complaint rate per unit", value = emp_panel$c_rate),
  data.table(source = "Simulated", metric = "Complaint rate per unit", value = panel$c_rate)
))
compare_rate_dt <- compare_rate_dt[is.finite(value)]

ggplot(compare_rate_dt, aes(x = value, color = source, fill = source)) +
  geom_density(alpha = 0.20, adjust = 1.1) +
  facet_wrap(~metric, scales = "free_x") +
  scale_fill_manual(values = c("Empirical" = "#264653", "Simulated" = "#D1495B")) +
  scale_color_manual(values = c("Empirical" = "#264653", "Simulated" = "#D1495B")) +
  labs(x = "Rate per unit", y = "Density", fill = NULL, color = NULL) +
  coord_cartesian(xlim = c(0, 0.75)) +
  theme_minimal(base_size = 11)
```

## Sorting Pattern

```{r sorting-figure, fig.cap="Distribution of equilibrium composition shares and realized filing rates by landlord type.", fig.align='center', out.width='92%'}
plot_type_dt <- melt(
  panel[, .(theta, s, f_rate)],
  id.vars = "theta",
  measure.vars = c("s", "f_rate"),
  variable.name = "metric",
  value.name = "value"
)
plot_type_dt[, metric := factor(
  metric,
  levels = c("s", "f_rate"),
  labels = c("Group-1 share", "Realized filing rate")
)]

ggplot(plot_type_dt, aes(x = value, color = theta, fill = theta)) +
  geom_density(alpha = 0.20, adjust = 1.1) +
  facet_wrap(~metric, scales = "free_x") +
  scale_fill_manual(values = c("G" = "#2A9D8F", "B" = "#D1495B")) +
  scale_color_manual(values = c("G" = "#2A9D8F", "B" = "#D1495B")) +
  labs(x = NULL, y = "Density", fill = "Type", color = "Type") +
  coord_cartesian(xlim = c(0, 0.75)) +
  theme_minimal(base_size = 11)
```

## Neighborhood Patterns

```{r nhood-summary-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_nhood_distribution_summary.tex"))
```

```{r nhood-figures, fig.cap="Neighborhood-level equilibrium variation in filing rates and group-1 share, using unit-weighted neighborhood means.", fig.align='center', out.width='95%'}
nhood_plot_dt <- melt(
  nhood_summary[, .(mean_f_rate, mean_s)],
  measure.vars = c("mean_f_rate", "mean_s"),
  variable.name = "metric",
  value.name = "value"
)
nhood_plot_dt[, metric := factor(
  metric,
  levels = c("mean_f_rate", "mean_s"),
  labels = c("Neighborhood mean filing rate", "Neighborhood mean group-1 share")
)]

ggplot(nhood_plot_dt, aes(x = value)) +
  geom_density(fill = "#3D405B", alpha = 0.70, color = NA, adjust = 1.1) +
  facet_wrap(~metric, scales = "free_x") +
  labs(x = NULL, y = "Density") +
  coord_cartesian(xlim = c(0, 0.75)) +
  theme_minimal(base_size = 11)
```

```{r nhood-empirical-vs-sim, fig.cap="Empirical vs simulated neighborhood distributions for unit-weighted neighborhood mean filing rates and neighborhood mean low-income shares.", fig.align='center', out.width='95%', fig.width=10, fig.height=7}
compare_nhood_dt <- rbindlist(list(
  data.table(source = "Empirical", metric = "Neighborhood mean filing rate", value = emp_nhood_summary$mean_f_rate),
  data.table(source = "Simulated", metric = "Neighborhood mean filing rate", value = nhood_summary$mean_f_rate),
  data.table(source = "Empirical", metric = "Neighborhood mean low-income share", value = emp_nhood_summary$mean_s),
  data.table(source = "Simulated", metric = "Neighborhood mean low-income share", value = nhood_summary$mean_s)
))

ggplot(compare_nhood_dt, aes(x = value, color = source, fill = source)) +
  geom_density(alpha = 0.20, adjust = 1.1) +
  facet_wrap(~metric, scales = "free_x") +
  scale_fill_manual(values = c("Empirical" = "#264653", "Simulated" = "#D1495B")) +
  scale_color_manual(values = c("Empirical" = "#264653", "Simulated" = "#D1495B")) +
  labs(x = NULL, y = "Density", fill = NULL, color = NULL) +
  coord_cartesian(xlim = c(0, 0.75)) +
  theme_minimal(base_size = 11)
```

```{r nhood-diagnostics, fig.cap="Neighborhood diagnostic views: ranked neighborhood group-1 shares and neighborhood mean filing rates against neighborhood mean group-1 shares.", fig.align='center', out.width='95%', fig.width=10, fig.height=8}
nhood_rank_dt <- copy(nhood_summary)[order(mean_s)]
nhood_rank_dt[, rank_s := .I]

p_rank <- ggplot(nhood_rank_dt, aes(x = rank_s, y = mean_s)) +
  geom_point(color = "#2A9D8F", alpha = 0.8, size = 1.5) +
  labs(x = "Neighborhood rank", y = "Neighborhood mean group-1 share") +
  theme_minimal(base_size = 11)

p_scatter <- ggplot(nhood_summary, aes(x = mean_s, y = mean_f_rate, size = total_units)) +
  geom_point(color = "#D1495B", alpha = 0.6) +
  geom_smooth(method = "lm", se = FALSE, color = "#3D405B", linewidth = 0.9) +
  labs(x = "Neighborhood mean group-1 share", y = "Neighborhood mean filing rate", size = "Units") +
  coord_cartesian(ylim = c(0, 0.75)) +
  theme_minimal(base_size = 11)

(p_rank + p_scatter) + patchwork::plot_layout(ncol = 1)
```

```{r nhood-filing-drivers, fig.cap="Neighborhood filing-rate variation against neighborhood bad-type share and by neighborhood size.", fig.align='center', out.width='95%', fig.width=10, fig.height=8}
p_bad_share <- ggplot(nhood_summary, aes(x = mean_theta_bad, y = mean_f_rate, size = total_units)) +
  geom_point(color = "#264653", alpha = 0.65) +
  geom_smooth(method = "lm", se = FALSE, color = "#E76F51", linewidth = 0.9) +
  labs(x = "Neighborhood mean bad-type share", y = "Neighborhood mean filing rate", size = "Units") +
  coord_cartesian(ylim = c(0, 0.75)) +
  theme_minimal(base_size = 11)

p_size_bin <- ggplot(nhood_summary[!is.na(size_bin)], aes(x = size_bin, y = mean_f_rate)) +
  geom_boxplot(fill = "#E9C46A", color = "#3D405B", outlier.alpha = 0.35) +
  labs(x = "Neighborhood total-units quartile", y = "Neighborhood mean filing rate") +
  coord_cartesian(ylim = c(0, 0.75)) +
  theme_minimal(base_size = 11)

(p_bad_share + p_size_bin) + patchwork::plot_layout(ncol = 1)
```

# First-Pass Calibration Targets

The first-pass calibration objective now uses a 16-moment target set:

1. Three marginal means: filing, maintenance, and complaint rates.
2. Three maintenance-intensity moments: the positive-part mean maintenance rate and the positive-part 50th and 90th percentiles.
3. Four neighborhood-dispersion moments: SD and 90-10 spread of neighborhood mean low-income shares and neighborhood mean filing rates.
4. Two sorting moments: composition on high filing within neighborhood, and composition for the top filing bin relative to the low filing bin within neighborhood.
5. Two complaint-gradient moments: complaints on composition, and complaints on composition $\times$ high filing.
6. One maintenance-discipline moment: maintenance counts on the raw complaint rate per unit, with neighborhood fixed effects and a unit offset.
7. One filing-dispersion moment: residual SD of filing rates after neighborhood fixed effects.

The zero-filing, zero-complaint, and zero-maintenance shares are still reported below as diagnostics, but they are no longer targeted directly in the objective. Once the panel is annualized over multiple years, those extensive-margin zeros are less informative than the level and dispersion moments.

The within-neighborhood sorting diagnostics are already in the calibration outputs: `sorting_coef_high_filing_nhood` and `sorting_coef_high_bin_nhood`. Those are the cleanest direct comparisons for whether the model is over- or under-sorting conditional on neighborhood fixed effects.

The current calibration target product is `r cfg$run$outer_sorting$calibration$target_product_key`, so the moment comparison table below should be read as an empirical fit diagnostic rather than a self-calibration check.

```{r moment-compare-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_moment_comparison_compact.tex"))
```

## Current Calibration Run

```{r calibration-run-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_calibration_run_summary.tex"), max_width = "0.75\\textwidth")
```

The current empirical calibration run did not fully converge in the optimizer. The fixed-point solver inside each simulation evaluation is behaving, but the outer optimizer stopped at convergence code `r opt_summary$convergence_code[1]` with objective `r sprintf("%.3f", opt_summary$objective_best[1])` after `r opt_summary$n_evaluations[1]` evaluations.

```{r calibrated-parameter-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_calibrated_parameter_changes.tex"))
```

```{r top-miss-table, results='asis'}
include_tex_table(file.path(tab_dir, "outer_sorting_top_moment_misses.tex"))
```

The largest misses are informative. In the current run, the model still overpredicts filing and maintenance rates, produces too little zero mass, and generates much stronger sorting gradients than the empirical target. The maintenance-discipline moment is also much smaller in the simulated equilibrium than in the data target.

# Current Interpretation

The baseline equilibrium does the basic qualitative work the model is supposed to do: bad-type buildings end up with higher filing rates and higher group-1 shares, while maintenance is lower on average in those buildings and complaints are higher. The citywide mass constraint is satisfied tightly and the deterministic fixed point converges quickly.

The empirical calibration results suggest that the current baseline is directionally coherent but still too aggressive relative to the data. The main gaps are in outcome levels, zero mass, sorting strength, and the complaint-maintenance discipline link.

The next substantive question is whether these misses come mostly from the empirical target construction, from the InfoUSA low-income-share proxy for composition, or from the structural tightness of the filing, complaint, and maintenance blocks themselves.
