---
title: "Retaliatory Evictions: Distributed-Lag Evidence"
author: "Philly Evictions Project"
date: today
format:
  pdf:
    pdf-engine: xelatex
    documentclass: article
    geometry: margin=1in
    fontsize: 11pt
    keep-tex: true
    number-sections: true
    toc: true
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
---

```{r setup, include=FALSE}
find_repo_root <- function(start = getwd()) {
  cur <- normalizePath(start, winslash = "/", mustWork = FALSE)
  for (i in 0:8) {
    has_cfg <- file.exists(file.path(cur, "config.yml")) || file.exists(file.path(cur, "config.example.yml"))
    has_markers <- file.exists(file.path(cur, "AGENTS.md")) || file.exists(file.path(cur, "README.md"))
    if (has_cfg && has_markers) return(cur)
    parent <- dirname(cur)
    if (identical(parent, cur)) break
    cur <- parent
  }
  stop("Could not infer repo root from working directory: ", start)
}

repo_root <- find_repo_root(getwd())
old_wd <- getwd()
setwd(repo_root)
on.exit(setwd(old_wd), add = TRUE)

knitr::opts_knit$set(root.dir = file.path(repo_root, "writeups"))
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 7,
  dpi = 300
)

suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
  library(kableExtra)
})

source(file.path(repo_root, "r", "config.R"))
cfg_path <- file.path(repo_root, if (file.exists(file.path(repo_root, "config.yml"))) "config.yml" else "config.example.yml")
cfg <- read_config(cfg_path, create_dirs = FALSE)

retaliatory_time_unit <- tolower(as.character(cfg$run$retaliatory_time_unit %||% "quarter"))
period_label <- if (retaliatory_time_unit == "quarter") "quarter" else "month"
period_plural <- if (retaliatory_time_unit == "quarter") "quarters" else "months"
period_title <- if (retaliatory_time_unit == "quarter") "Quarter" else "Month"
retaliatory_stub <- paste0("retaliatory_", if (retaliatory_time_unit == "quarter") "quarterly" else "monthly")
out_dir <- p_out(cfg, "retaliatory-evictions")
fallback_out_dir <- normalizePath(file.path(repo_root, "output", "retaliatory-evictions"), winslash = "/", mustWork = FALSE)
if (grepl("/writeups/output(/|$)", out_dir) && dir.exists(fallback_out_dir)) {
  out_dir <- fallback_out_dir
} else if (!dir.exists(out_dir) && dir.exists(fallback_out_dir)) {
  out_dir <- fallback_out_dir
}
if (!dir.exists(out_dir)) {
  stop("Retaliatory output directory not found: ", out_dir, " (fallback checked: ", fallback_out_dir, ")")
}

tab_out_dir <- file.path(out_dir, "tables")
fig_out_dir <- file.path(out_dir, "figs")

retaliatory_out <- function(suffix) {
  ext <- tolower(tools::file_ext(suffix))
  base <- paste0(retaliatory_stub, "_", suffix)
  if (ext %chin% c("png", "jpg", "jpeg", "svg", "pdf")) {
    file.path(fig_out_dir, base)
  } else {
    file.path(tab_out_dir, base)
  }
}

pick_existing <- function(paths) {
  for (p in paths) if (file.exists(p)) return(p)
  NA_character_
}

require_existing <- function(paths, label) {
  hit <- pick_existing(paths)
  if (is.na(hit)) {
    stop(label, " not found. Tried paths:\n", paste(paths, collapse = "\n"))
  }
  hit
}

to_writeups_rel <- function(path) {
  abs_path <- normalizePath(path, winslash = "/", mustWork = TRUE)
  writeups_dir <- normalizePath(file.path(repo_root, "writeups"), winslash = "/", mustWork = TRUE)
  as.character(fs::path_rel(abs_path, start = writeups_dir))
}

fmt_pct <- function(x) sprintf("%.1f%%", 100 * x)
```

# Overview

This writeup now reports only the retaliatory timing analysis from `r/retaliatory-evictions.r`:

- distributed-lag event-time regressions (`filed_eviction` on lags/leads of complaint indicators)
- bandwidth diagnostics around eviction filings
- distributed-lag heterogeneity by building-level `% Black` split

Complaint-suppression analysis was intentionally removed from this workflow and now lives in `r/comp-statics-annual-race.R` and `writeups/comp-statics-annual-race.qmd`.
Unless explicitly overridden in the script call, outputs shown here are pre-COVID only (`<= 2019`).

# Empirical Bayes Filing-Rate Memo

The maintenance regressions below now use `filing_rate_eb_pre_covid` as the default filing-intensity measure. This is the building-level Empirical Bayes (Gamma-Poisson) posterior mean pooled over pre-2019 years:

$$
y_{it} \mid \lambda_i \sim \text{Poisson}(E_{it}\lambda_i), \qquad
\lambda_i \sim \text{Gamma}(\alpha,\beta),
$$

with sufficient statistics

$$
Y_i=\sum_t y_{it}, \qquad E_i=\sum_t E_{it},
$$

and posterior mean

$$
\mathbb{E}[\lambda_i\mid Y_i,E_i]=\frac{\alpha+Y_i}{\beta+E_i}.
$$

In the production pipeline (`r/make-analytic-sample.R`, section 6b), the city prior is estimated by method-of-moments; ZIP-specific priors are used when supported, otherwise the city prior is used as fallback. The raw long-run filing rate remains available for robustness and is reported in the appendix of this writeup.

Reference memo for reuse: `docs/notes/eb-filing-rate-memo-2026-03-04.md`.

# Estimating Equations

## Distributed lag (main)

For complaint stem $c \in \{\text{complaint},\text{severe},\text{non\_severe}\}$:

$$
Y_{it}
=
\sum_{k=1}^{h}\beta^{-}_{k,c} D^c_{i,t-k}
+ \beta^{0}_{c} D^c_{i,t}
+ \sum_{k=1}^{h}\beta^{+}_{k,c} D^c_{i,t+k}
+ \alpha_i + \gamma_t + \varepsilon_{it},
$$

where:

- $Y_{it}=\mathbb{1}[\text{filed\_eviction}_{it}=1]$
- $D^c_{it}=\mathbb{1}[\text{filed\_}c_{it}=1]$
- $\alpha_i$: PID fixed effects, $\gamma_t$: period fixed effects
- SEs clustered at PID

## Race heterogeneity split

Define:

$$
G_{it}=\mathbb{1}[\text{infousa\_pct\_black}_{it} \ge c_{\text{pre}}],
$$

where $c_{\text{pre}}$ is computed from pre-2020 $(PID,year)$-unique observations using the configured rule (default: pre-COVID mean).

The same distributed-lag equation is estimated on high- and low-$G_{it}$ subsamples.

# Data and Sample

- Unit: PID $\times$ `r period_label`
- Default window: 2011--2019
- Inputs: rental building panel, analytic PID filter, eviction filings + address crosswalk, and `bldg_panel_blp` tenant composition
- Eviction filing sample restrictions (implemented in `r/retaliatory-evictions.r`):
  - keep only filings with unique parcel crosswalk matches (`num_parcels_matched == 1`)
  - drop commercial filings (`commercial != TRUE`)
  - drop non-residential filings (`non_residential != TRUE`)
  - keep only non-payment-of-rent filings (`a == TRUE` in `evictions_clean`)
  - apply the configured year window (default pre-COVID: 2011--2019)
- `Full` complaint indicator: any complaint filing in the period.
- `Severe` complaint indicator: any period complaint in the severe bundle (`heat`, `fire`, or `property_maintenance`), consistent with `total_severe_complaints` in the panel.
- `Non-Severe` complaint indicator: any complaint in the non-severe bundle used in the script.

This aligns the filing sample with the non-payment focus in Lodermeier (2025) and with the eviction data README note that complaint-derived fields are consistently available from 2006 onward, with a complaint format change in 2011.

```{r sample-restrictions}
filter_path <- require_existing(c(
  retaliatory_out("eviction_case_filter_counts.csv"),
  file.path(out_dir, "retaliatory_quarterly_eviction_case_filter_counts.csv"),
  file.path(out_dir, "retaliatory_monthly_eviction_case_filter_counts.csv")
), "Eviction case filter counts")

filt <- fread(filter_path)
filt_show <- filt[, .(
  Step = step,
  `Rows` = format(n_rows, big.mark = ","),
  `Share of raw` = sprintf("%.1f%%", 100 * retained_share_from_raw)
)]
kable(filt_show, format = "latex", booktabs = TRUE,
      caption = "Eviction filing sample restrictions used in this analysis") |>
  kable_styling(latex_options = c("hold_position", "striped"), font_size = 8)
```

# Bandwidth Diagnostics

```{r bandwidth-summary}
band_path <- require_existing(c(
  retaliatory_out("bandwidth_summary.csv"),
  file.path(out_dir, "retaliatory_quarterly_bandwidth_summary.csv"),
  file.path(out_dir, "retaliatory_monthly_bandwidth_summary.csv")
), "Bandwidth summary")

band <- fread(band_path)
show <- band[, .(
  `Bandwidth` = bandwidth_periods,
  `Same period` = fmt_pct(same_period_share),
  `Within bandwidth` = fmt_pct(within_bw_share),
  `Within bandwidth, not same period` = fmt_pct(plausible_only_share),
  `Non-retaliatory` = fmt_pct(non_retaliatory_share)
)]
kable(show, format = "latex", booktabs = TRUE,
      caption = sprintf("Eviction filing decomposition within %s windows", period_plural)) |>
  kable_styling(latex_options = c("hold_position", "striped"), font_size = 9)
```

# Distributed-Lag Results

```{r distlag-plot, fig.cap="Distributed-lag coefficients (pre-COVID): effect of complaint indicators at lag/lead k on eviction filing indicator. Panels are labeled Full, Non-Severe, and Severe. PID and period FE; SE clustered by PID.", out.width="100%", fig.align="center"}
dist_plot <- require_existing(c(
  retaliatory_out("distlag_coefficients.png"),
  file.path(out_dir, "retaliatory_quarterly_distlag_coefficients.png"),
  file.path(out_dir, "retaliatory_monthly_distlag_coefficients.png")
), "Distributed-lag plot")

knitr::include_graphics(to_writeups_rel(dist_plot))
```

# `% Black` Heterogeneity in Distributed Lags

```{r distlag-black-plot, fig.cap="Distributed-lag coefficients by high/low pct black split (cutoff from pre-COVID distribution rule configured in script).", out.width="100%", fig.align="center"}
dist_black_plot <- require_existing(c(
  retaliatory_out("distlag_coefficients_black_split.png"),
  file.path(out_dir, "retaliatory_quarterly_distlag_coefficients_black_split.png"),
  file.path(out_dir, "retaliatory_monthly_distlag_coefficients_black_split.png")
), "Distributed-lag % Black split plot")

knitr::include_graphics(to_writeups_rel(dist_black_plot))
```

# One-Month Back-Rent Regressions

Case assignment for this block:

- Outcome: `one_month_back_rent = 1` when `total_rent / ongoing_rent` is within `1 ± tol` (default `tol = 0.10`).
- `retaliatory_severe = 1` if an eviction case's PID-period has a severe complaint in the same period or within `± bandwidth` periods (default bandwidth is `2` quarters).
- `high_black_split = 1` if building `infousa_pct_black` is above the pre-COVID mean cutoff.
- Defendant race category from case-level imputation (`r/impute-race.R` output): `black` if `case_p_black >= 0.8`, `white` if `case_p_white >= 0.8`, and `unknown` otherwise.
- In the defendant-race interaction model, `white` is the reference category.

```{r one-month-retaliatory-status}
status_path <- require_existing(c(
  retaliatory_out("case_retaliatory_status_summary.csv"),
  file.path(out_dir, "retaliatory_quarterly_case_retaliatory_status_summary.csv"),
  file.path(out_dir, "retaliatory_monthly_case_retaliatory_status_summary.csv")
), "Case retaliatory status summary")

st <- fread(status_path)
st_show <- st[, .(
  Status = retaliatory_status,
  Cases = n_cases,
  Share = sprintf("%.1f%%", 100 * share)
)]
kable(st_show, format = "latex", booktabs = TRUE,
      caption = "Pre-COVID case assignment by severe-complaint proximity") |>
  kable_styling(latex_options = c("hold_position", "striped"), font_size = 8)
```

```{r one-month-retaliatory-sample}
sample_path <- require_existing(c(
  retaliatory_out("case_one_month_retaliatory_sample_summary.csv"),
  file.path(out_dir, "retaliatory_quarterly_case_one_month_retaliatory_sample_summary.csv"),
  file.path(out_dir, "retaliatory_monthly_case_one_month_retaliatory_sample_summary.csv")
), "Case one-month retaliatory sample summary")

ss <- fread(sample_path)
spec_map <- c(
  one_month_on_retaliatory_severe = "Status dummies only",
  one_month_on_retaliatory_severe_x_high_black = "Status x building above-mean pct black",
  one_month_on_retaliatory_severe_x_defendant_race_grp = "Status x defendant race group (white ref)"
)

fmt_pct_na <- function(x) ifelse(is.na(x), "--", sprintf("%.1f%%", 100 * x))
ss_show <- ss[, .(
  Spec = fifelse(spec %chin% names(spec_map), unname(spec_map[spec]), spec),
  N = n_obs,
  `Mean(1 month rent)` = round(mean_outcome, 4),
  `Same-period severe share` = fmt_pct_na(same_period_share),
  `Within-bw severe (not same period) share` = fmt_pct_na(bw_not_same_period_share),
  `Above-mean pct black share` = fmt_pct_na(high_black_share),
  `Defendant race: Black` = fmt_pct_na(defendant_race_black_share),
  `Defendant race: White` = fmt_pct_na(defendant_race_white_share),
  `Defendant race: Unknown` = fmt_pct_na(defendant_race_unknown_share),
  `Defendant race impute-ok share` = fmt_pct_na(defendant_race_ok_share)
)]

kable(ss_show, format = "latex", booktabs = TRUE,
      caption = "Regression sample summary (pre-COVID; PID + year FE specs)") |>
  kable_styling(latex_options = c("hold_position", "striped", "scale_down"), font_size = 8)
```

```{r one-month-retaliatory-etable, results='asis'}
etable_tex_path <- require_existing(c(
  retaliatory_out("case_one_month_retaliatory_model_table.tex"),
  file.path(out_dir, "retaliatory_quarterly_case_one_month_retaliatory_model_table.tex"),
  file.path(out_dir, "retaliatory_monthly_case_one_month_retaliatory_model_table.tex")
), "Case one-month retaliatory etable (tex)")

etable_lines <- readLines(etable_tex_path, warn = FALSE)
tab_start <- which(grepl("^\\\\begin\\{tabular\\}", etable_lines))[1]
tab_end <- tail(which(grepl("^\\\\end\\{tabular\\}", etable_lines)), 1)

if (is.finite(tab_start) && is.finite(tab_end) && tab_end >= tab_start) {
  tab_block <- etable_lines[tab_start:tab_end]
  cat("\\begin{center}\n")
  cat("\\resizebox{\\linewidth}{!}{%\n")
  cat(paste(tab_block, collapse = "\n"))
  cat("\n}\n")
  cat("\\end{center}\n")
} else {
  cat(paste(etable_lines, collapse = "\n"))
}
```

## Poisson (PPML) Regressions: Months Back Rent

The same three specifications are repeated using Poisson (PPML) with `months_back_rent` (= `total_rent / ongoing_rent`, continuous) as the outcome. Coefficients are log-multiplicative; SEs clustered by PID.

```{r pois-retaliatory-etable, results='asis'}
pois_etable_tex_path <- require_existing(c(
  retaliatory_out("case_one_month_retaliatory_pois_model_table.tex"),
  file.path(out_dir, "retaliatory_quarterly_case_one_month_retaliatory_pois_model_table.tex"),
  file.path(out_dir, "retaliatory_monthly_case_one_month_retaliatory_pois_model_table.tex")
), "Case months-back-rent Poisson etable (tex)")

pois_etable_lines <- readLines(pois_etable_tex_path, warn = FALSE)
pois_tab_start <- which(grepl("^\\\\begin\\{tabular\\}", pois_etable_lines))[1]
pois_tab_end <- tail(which(grepl("^\\\\end\\{tabular\\}", pois_etable_lines)), 1)

if (is.finite(pois_tab_start) && is.finite(pois_tab_end) && pois_tab_end >= pois_tab_start) {
  pois_tab_block <- pois_etable_lines[pois_tab_start:pois_tab_end]
  cat("\\begin{center}\n")
  cat("\\resizebox{\\linewidth}{!}{%\n")
  cat(paste(pois_tab_block, collapse = "\n"))
  cat("\n}\n")
  cat("\\end{center}\n")
} else {
  cat(paste(pois_etable_lines, collapse = "\n"))
}
```

## OLS Log-Rent Regression: log(Total Rent) | log(Ongoing Rent)

Outcome is `log(total_rent)` with `log(ongoing_rent)` entered as a continuous covariate. Conditioning on log ongoing rent removes the mechanical correlation between total back rent and rent level across tenants. The coefficient on `retaliatory_status` therefore captures the percentage difference in total back rent *claimed* for retaliatory versus non-retaliatory cases, holding the monthly rent fixed. A negative coefficient means landlords file for less back rent in retaliatory cases — i.e., the filing is not primarily about recovering arrears.

```{r log-rent-retaliatory-etable, results='asis'}
log_rent_tex_path <- require_existing(c(
  retaliatory_out("case_log_rent_retaliatory_model_table.tex"),
  file.path(out_dir, "retaliatory_quarterly_case_log_rent_retaliatory_model_table.tex"),
  file.path(out_dir, "retaliatory_monthly_case_log_rent_retaliatory_model_table.tex")
), "Case log-rent retaliatory etable (tex)")

log_rent_lines <- readLines(log_rent_tex_path, warn = FALSE)
lr_tab_start <- which(grepl("^\\\\begin\\{tabular\\}", log_rent_lines))[1]
lr_tab_end   <- tail(which(grepl("^\\\\end\\{tabular\\}", log_rent_lines)), 1)

if (is.finite(lr_tab_start) && is.finite(lr_tab_end) && lr_tab_end >= lr_tab_start) {
  lr_tab_block <- log_rent_lines[lr_tab_start:lr_tab_end]
  cat("\\begin{center}\n")
  cat("\\resizebox{\\linewidth}{!}{%\n")
  cat(paste(lr_tab_block, collapse = "\n"))
  cat("\n}\n")
  cat("\\end{center}\n")
} else {
  cat(paste(log_rent_lines, collapse = "\n"))
}
```

# Equilibrium Maintenance Analysis

This section examines whether landlords adjust maintenance investment (proxied by permit activity) in response to eviction pressure and tenant composition, and whether permit activity responds dynamically to severe complaints.

## Baseline Maintenance Permit Regressions

Poisson (PPML) regressions of `total_permits` on building-level eviction filing intensity and racial composition, with `log(total_units)` as offset. Main specifications use EB pre-COVID filing intensity (`filing_rate_eb_pre_covid`) with:

- a high-filing dummy (`>= 15%`)
- filing bins: `[0,1)`, `[1,5)`, `[5,10)`, `[10,20)`, `[20,inf)` (all on EB rates)

The rent-augmented variants add mean inflation-adjusted log rent (within PID over 2011--2019) to partial out rent-driven maintenance incentives.

```{r maintenance-etable, results='asis'}
maint_tex_path <- pick_existing(c(
  retaliatory_out("maintenance_model_table.tex"),
  file.path(out_dir, "retaliatory_quarterly_maintenance_model_table.tex"),
  file.path(out_dir, "retaliatory_monthly_maintenance_model_table.tex")
))

if (!is.na(maint_tex_path)) {
  maint_lines <- readLines(maint_tex_path, warn = FALSE)
  tab_start <- which(grepl("^\\\\begin\\{tabular\\}", maint_lines))[1]
  tab_end   <- tail(which(grepl("^\\\\end\\{tabular\\}", maint_lines)), 1)
  if (is.finite(tab_start) && is.finite(tab_end) && tab_end >= tab_start) {
    cat("\\begin{center}\n")
    cat("\\resizebox{\\linewidth}{!}{%\n")
    cat(paste(maint_lines[tab_start:tab_end], collapse = "\n"))
    cat("\n}\n")
    cat("\\end{center}\n")
  } else {
    cat(paste(maint_lines, collapse = "\n"))
  }
} else {
  cat("\\textit{Maintenance model table not found; re-run retaliatory-evictions.r.}\n")
}
```

## Landlord Response to Severe Complaints

The following coefplot shows estimates from a PPML regression of `total_permits` on contemporaneous, lagged (past quarters), and lead (future quarters) severe complaint counts, with PID and year fixed effects. Lead terms serve as pre-trend checks.

```{r landlord-response-plot, fig.cap="Landlord maintenance response to severe complaints: PPML event-study. Negative timing = complaints occur in future periods relative to permit outcome (pre-trend check); positive timing = past complaints. PID + year FE; offset = log(total_units); 95% CI.", out.width="100%", fig.align="center"}
lr_plot_path <- pick_existing(c(
  retaliatory_out("landlord_response_plot.png"),
  file.path(out_dir, "retaliatory_quarterly_landlord_response_plot.png"),
  file.path(out_dir, "retaliatory_monthly_landlord_response_plot.png")
))

if (!is.na(lr_plot_path)) {
  knitr::include_graphics(to_writeups_rel(lr_plot_path))
} else {
  cat("\\textit{Landlord response plot not found; re-run retaliatory-evictions.r.}\n")
}
```

# Notes

- Raw long-run filing-rate maintenance regressions are moved to the appendix section below.
- This writeup intentionally excludes same-period, targeting, LP-DiD, and complaint-suppression blocks.
- For complaint-suppression specifications and interpretation, use `writeups/comp-statics-annual-race.qmd`.

# Appendix: Raw Filing Robustness

These regressions mirror the baseline maintenance models but replace EB filing intensity with raw long-run pre-2019 filing rate (same 15% high-filing cutoff and same bins), for robustness only.

```{r maintenance-etable-raw-appendix, results='asis'}
maint_raw_tex_path <- pick_existing(c(
  retaliatory_out("maintenance_model_table_raw.tex"),
  file.path(out_dir, "retaliatory_quarterly_maintenance_model_table_raw.tex"),
  file.path(out_dir, "retaliatory_monthly_maintenance_model_table_raw.tex")
))

if (!is.na(maint_raw_tex_path)) {
  maint_raw_lines <- readLines(maint_raw_tex_path, warn = FALSE)
  tab_start <- which(grepl("^\\\\begin\\{tabular\\}", maint_raw_lines))[1]
  tab_end   <- tail(which(grepl("^\\\\end\\{tabular\\}", maint_raw_lines)), 1)
  if (is.finite(tab_start) && is.finite(tab_end) && tab_end >= tab_start) {
    cat("\\begin{center}\n")
    cat("\\resizebox{\\linewidth}{!}{%\n")
    cat(paste(maint_raw_lines[tab_start:tab_end], collapse = "\n"))
    cat("\n}\n")
    cat("\\end{center}\n")
  } else {
    cat(paste(maint_raw_lines, collapse = "\n"))
  }
} else {
  cat("\\textit{Raw maintenance robustness table not found; re-run retaliatory-evictions.r.}\n")
}
```
