---
title: "Severe Complaint-Maintenance Diagnostics"
author: "Philly Evictions Project"
date: today
format:
  pdf:
    pdf-engine: xelatex
    documentclass: article
    geometry: margin=1in
    fontsize: 11pt
    keep-tex: true
    number-sections: true
    toc: true
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{adjustbox}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 6,
  dpi = 300
)
```

# Overview

This writeup isolates the maintenance-complaint relationship using **severe complaints only**, before returning to demographic regressions.

The underlying script is `r/severe-maintenance-diagnostics.R`.

Design choices in this version:

- Outcome: `total_severe_complaints` (quarterly count)
- Panel + controls source: quarterly rental panel (`building_data_rental_quarter`) with annual controls merged from `bldg_panel_blp` (`PID x year`)
- Maintenance flow baseline: repair-ish permit counts only (`electrical`, `plumbing`, `mechanical`, `fire_suppression`); a broad flow variant adds `building_permit_count` for robustness
- Maintenance scaling: per-unit rates using annual `total_units` (`maint_rate_* = permit_flow / total_units_ann`, with `total_units_ann` floored at 1)
- Lag/lead maintenance variables: `t-1` flow, `t-1:t-4` average lagged flow, and leads (`t+1`, `t+2`) for falsification
- Rolling maintenance stock: EWMA of **lagged** repair flow (`maint_stock_lag`) within `PID`, then scaled by units (`maint_stock_lag_rate`); default decay parameter is `lambda = 0.9` (CLI-overridable)
- Unit controls: nonlinear spline in `log(1 + total_units)` (`df = 4`) plus deterministic fine unit bins (`1`, `2`, ..., `10`, `11-12`, `13-15`, ..., `151-200`, `201+`, `Unknown`) used in the stock-focused specifications
- Quality controls: coarsened `A/B/C/D/E/Other` grades (dropping `+/-`) throughout the diagnostics
- Estimation: `fepois` with cluster-robust SEs by `PID`, weighted by annual units
- Diagnostics added: lead falsification, PID+period FE (within-building) regressions, support tables for quality x fine-unit-bin cells
- Parcel-controls diagnostics: the default fast-mode stock table includes a parcel-controls stock spec with `log(total_area)` (no market-value control)
- Runtime note: `r/severe-maintenance-diagnostics.R` defaults to `--fast_mode=TRUE`, which fits and writes tables in batches, skips the slowest stock-quality interaction variants / rich-interaction or rent variants / PID FE variants, and omits the partial-correlation figure; use `--fast_mode=FALSE` for the full suite

```{r load-helpers}
suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
  library(kableExtra)
})
qmd_path <- knitr::current_input(dir = TRUE)
proj_root <- normalizePath(file.path(dirname(qmd_path), ".."), winslash = "/", mustWork = FALSE)
source(file.path(proj_root, "r", "config.R"))
old_wd <- getwd()
setwd(proj_root)
on.exit(setwd(old_wd), add = TRUE)
cfg <- read_config(file.path(proj_root, "config.yml"))
tab_dir <- normalizePath(file.path(proj_root, "output", "tables"), winslash = "/", mustWork = FALSE)
fig_dir <- normalizePath(file.path(proj_root, "output", "figs"), winslash = "/", mustWork = FALSE)

include_tex_table <- function(path, max_width = "\\textwidth") {
  if (!file.exists(path)) { cat("Table not found:", path); return(invisible(NULL)) }
  lines <- readLines(path)
  txt <- paste(lines, collapse = "\n")
  has_float <- grepl("\\\\begin\\{table\\}", txt)
  if (has_float) {
    is_float <- grepl("^\\s*\\\\begin\\{table\\}|^\\s*\\\\end\\{table\\}", lines)
    is_meta <- grepl("^\\s*\\\\caption|^\\s*\\\\label|^\\s*\\\\centering", lines)
    cap_lines <- trimws(lines[is_meta])
    inner <- lines[!is_float & !is_meta]
    cat("\\begin{table}[htbp]\n\\centering\n")
    cat(cap_lines, sep = "\n")
    cat("\n\\begin{adjustbox}{max width=", max_width, "}\n", sep = "")
    cat(inner, sep = "\n")
    cat("\n\\end{adjustbox}\n\\end{table}\n")
  } else {
    cat("\\begin{adjustbox}{max width=", max_width, "}\n", sep = "")
    cat(lines, sep = "\n")
    cat("\n\\end{adjustbox}\n")
  }
}

include_fig_if_exists <- function(path, missing_msg = "Figure not found.") {
  if (file.exists(path)) knitr::include_graphics(path) else cat(missing_msg)
}
```

# Sample Diagnostics

```{r sample-diag}
sample_path <- file.path(tab_dir, "severe_maint_diag_sample.csv")
if (file.exists(sample_path)) {
  dd <- fread(sample_path)
  dd[, `:=`(
    share_nonzero_severe = round(share_nonzero_severe, 4),
    share_zero_curr_maint = round(share_zero_curr_maint, 4),
    share_zero_l1_maint = round(share_zero_l1_maint, 4)
  )]
  kable(dd, booktabs = TRUE, caption = "Severe-maintenance diagnostic sample summary") |>
    kable_styling(latex_options = c("hold_position", "scale_down"))
} else {
  cat("Run `r/severe-maintenance-diagnostics.R` first.")
}
```

## Support By Quality And Unit Bin

These diagnostics are included to assess whether stock-by-quality interactions are identified on meaningful support (especially after restricting those interaction specs to the controls-matched subset).

```{r support-quality}
path_q <- file.path(tab_dir, "severe_maint_diag_support_by_quality.csv")
if (file.exists(path_q)) {
  x <- fread(path_q)
  num_cols <- setdiff(names(x), "quality_grade_abcde")
  for (cc in num_cols) if (is.numeric(x[[cc]])) x[, (cc) := round(get(cc), 4)]
  kable(x, booktabs = TRUE, caption = "Support diagnostics by coarsened quality grade (full severe-diagnostic sample)") |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8)
} else {
  cat("Run `r/severe-maintenance-diagnostics.R` first.")
}
```

```{r support-thin-cells}
path_thin <- file.path(tab_dir, "severe_maint_diag_support_thin_cells.csv")
if (file.exists(path_thin)) {
  x <- fread(path_thin)
  kable(x, booktabs = TRUE, caption = "Thin-cell summary for quality-grade x fine-unit-bin cells (controls-matched subset used in stock-quality interaction specs)") |>
    kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8)
} else {
  cat("Run `r/severe-maintenance-diagnostics.R` first.")
}
```

# Main Severe-Maintenance Diagnostics

This is the default **stock-focused** table from fast mode. It reports three rolling-stock specifications:

- baseline stock spec with nonlinear unit controls + period and coarse quality-grade FE
- stock spec with fine unit-bin FE
- parcel-controls stock spec with `log(total_area)` plus `year_blt_decade`, coarse quality-grade FE, fine unit-bin FE, and period FE

In full mode (`--fast_mode=FALSE`), this table expands to include stock-by-quality interaction and richer-control variants.

```{r main-models, results='asis'}
include_tex_table(file.path(tab_dir, "severe_maint_diag_models.tex"))
```

# Auxiliary Flow Diagnostics

This section holds the **auxiliary flow-based diagnostics** (current and lagged flows, plus broad-permit proxy), which are useful for reverse-causality checks but are not the primary stock-based specifications.

- contemporaneous maintenance flow
- lagged flow (`t-1`) and rolling lagged flow average (`t-1` to `t-4`)
- joint current + stock specification
- broad permit proxy comparison

```{r stock-quality-models, results='asis'}
include_tex_table(file.path(tab_dir, "severe_maint_diag_stock_quality_models.tex"))
```

# Falsification And Within-Building Diagnostics

This section reports:

- lead maintenance (`t+1`, `t+2`) falsification regressions
- PID+period FE (within-building) regressions using lagged and lead maintenance signals

In default fast mode, this section is a placeholder table (the expensive falsification / PID FE regressions are skipped).

```{r fals-pid-models, results='asis'}
include_tex_table(file.path(tab_dir, "severe_maint_diag_falsification_pidfe_models.tex"))
```

# Partial-Correlation Plot

This figure is omitted in default fast mode and appears only in full mode (`--fast_mode=FALSE`).

```{r partial-corr-fig, fig.cap="Partial-correlation diagnostics for severe complaints vs current, lagged, and cumulative lagged repair permits per unit. Both axes are residualized on nonlinear unit controls with period and quality-grade fixed effects, then summarized in weighted bins.", out.width="95%", fig.align="center"}
include_fig_if_exists(
  file.path(fig_dir, "severe_maint_diag_partial_corr.png"),
  "Partial-correlation figure not found. Run `r/severe-maintenance-diagnostics.R` first."
)
```

# Notes

- Category-specific complaint counts exist in the quarterly product, but category-specific **severe** complaint counts are not available in the current product, so this writeup remains severe-total only.
- Stock-by-quality interaction specs are estimated on the controls-matched subset with non-`Unknown` fine unit bins, to avoid collapsing identification onto the missing-controls mass.
- This is a diagnostics workflow intended to decide which maintenance specifications are worth carrying into later complaint or demographic analyses.
