---
title: "Ownership Transfers and Eviction Filing Rates"
author: "Philly Evictions Project"
date: today
format:
  pdf:
    pdf-engine: xelatex
    documentclass: article
    geometry: margin=1in
    fontsize: 11pt
    keep-tex: true
    number-sections: true
    toc: true
    include-in-header:
      text: |
        \usepackage{booktabs}
        \usepackage{longtable}
        \usepackage{adjustbox}
        \usepackage{pdflscape}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 10,
  fig.height = 7,
  dpi = 300,
  out.width = "95%"
)
```

```{r load-data}
suppressPackageStartupMessages({
  library(data.table)
  library(knitr)
  library(kableExtra)
})

qmd_path <- knitr::current_input(dir = TRUE)
proj_root <- normalizePath(file.path(dirname(qmd_path), ".."), winslash = "/", mustWork = FALSE)
source(file.path(proj_root, "r", "config.R"))
old_wd <- getwd()
setwd(proj_root)
on.exit(setwd(old_wd), add = TRUE)
cfg <- read_config(file.path(proj_root, "config.yml"))

out_dir <- file.path(proj_root, "output", "transfer_evictions")
fig_dir <- file.path(out_dir, "figs")
sample_year_min <- 2006L
sample_year_max <- 2019L
event_ref_period <- -2L
event_window_min <- -3L
event_window_max <- 3L

must_read <- function(path) {
  if (!file.exists(path)) stop("Missing required output: ", path)
  fread(path)
}

include_tex_table <- function(path, max_width = "\\textwidth", landscape = FALSE, size = NULL) {
  if (!file.exists(path)) stop("Missing required table: ", path)
  lines <- readLines(path)
  txt <- paste(lines, collapse = "\n")
  has_float <- grepl("\\\\begin\\{table\\}", txt)
  width_use <- if (landscape && identical(max_width, "\\textwidth")) "0.95\\linewidth" else max_width
  if (landscape) cat("\\begin{landscape}\n")
  if (has_float) {
    is_float <- grepl("^\\s*\\\\begin\\{table\\}|^\\s*\\\\end\\{table\\}", lines)
    is_meta <- grepl("^\\s*\\\\caption|^\\s*\\\\label|^\\s*\\\\centering", lines)
    cap_lines <- trimws(lines[is_meta])
    inner <- lines[!is_float & !is_meta]
    cat("\\begin{table}[htbp]\n\\centering\n")
    cat(cap_lines, sep = "\n")
    if (!is.null(size)) cat("\n\\", size, "\n", sep = "")
    cat("\n\\begin{adjustbox}{max width=", width_use, "}\n", sep = "")
    cat(inner, sep = "\n")
    cat("\n\\end{adjustbox}\n\\end{table}\n")
  } else {
    if (!is.null(size)) cat("\\", size, "\n", sep = "")
    cat("\\begin{adjustbox}{max width=", width_use, "}\n", sep = "")
    cat(lines, sep = "\n")
    cat("\n\\end{adjustbox}\n")
  }
  if (landscape) cat("\\end{landscape}\n")
}

must_graphic <- function(path) {
  if (!file.exists(path)) stop("Missing required figure: ", path)
  knitr::include_graphics(path)
}

add_et <- function(dt) {
  out <- copy(dt)
  if (!"et" %in% names(out) && "term" %in% names(out)) {
    out[, et := suppressWarnings(as.integer(sub(".*::", "", term)))]
  }
  out
}

label_map_core <- c(
  core_all_units = "All buildings",
  core_1unit = "1-unit",
  core_2plus = "2+ units",
  core_2plus_rental_evidence = "2+ units, rental evidence",
  core_5plus = "5+ units",
  core_5plus_rental_evidence = "5+ units, rental evidence",
  core_10plus = "10+ units",
  core_10plus_rental_evidence = "10+ units, rental evidence"
)
label_map_acq <- c(
  full = "All acquirers",
  highfiler_portfolio_10plus_otherunits = "High-filer portfolio",
  lowfiler_portfolio_10plus_otherunits = "Low-filer portfolio",
  smallportfolio_lt10_otherunits = "Small portfolio",
  singlepurchase = "Single-purchase"
)
fmt_num <- function(x, digits = 1) formatC(x, format = "f", digits = digits, big.mark = ",")
fmt_int <- function(x) formatC(as.integer(round(x)), format = "d", big.mark = ",")

event_summary <- function(dt, spec_labels, ets = c(1L, 2L, 3L)) {
  out <- copy(dt)[et %in% ets & spec %in% names(spec_labels),
                  .(spec, et, estimate = round(estimate, 4), std_error = round(std_error, 4))]
  out[, spec := spec_labels[spec]]
  dcast(out, spec ~ et, value.var = "estimate")
}

filing_core <- add_et(must_read(file.path(out_dir, "annual_filing_core_coefs.csv")))
filing_acq <- add_et(must_read(file.path(out_dir, "annual_filing_acq_2plus_coefs.csv")))
acq_cutoffs <- must_read(file.path(out_dir, "annual_acq_cutoffs.csv"))

occupancy <- add_et(must_read(file.path(out_dir, "annual_occupancy_2plus_coefs.csv")))
pct_black <- add_et(must_read(file.path(out_dir, "annual_pct_black_2plus_coefs.csv")))
pct_asian <- add_et(must_read(file.path(out_dir, "annual_pct_asian_2plus_coefs.csv")))
pct_latino <- add_et(must_read(file.path(out_dir, "annual_pct_latino_2plus_coefs.csv")))
pct_white <- add_et(must_read(file.path(out_dir, "annual_pct_white_2plus_coefs.csv")))
permit <- add_et(must_read(file.path(out_dir, "annual_permit_rate_2plus_coefs.csv")))
complaint <- add_et(must_read(file.path(out_dir, "annual_complaint_rate_2plus_coefs.csv")))
rent_core <- add_et(must_read(file.path(out_dir, "annual_rent_core_coefs.csv")))
rent_safe <- add_et(must_read(file.path(out_dir, "annual_rent_safe_core_coefs.csv")))
rental_evidence_1unit <- add_et(must_read(file.path(out_dir, "annual_rental_evidence_1unit_coefs.csv")))
rental_evidence_2plus <- add_et(must_read(file.path(out_dir, "annual_rental_evidence_2plus_coefs.csv")))

filing_sample_rows <- unique(filing_core[, .(spec, n, treated_pids, control_pids)])
filing_sample_rows[, sample := label_map_core[spec]]
filing_sample_rows <- filing_sample_rows[, .(sample, treated_pids, control_pids, stacked_rows = n)]

filing_acq_rows <- unique(filing_acq[, .(spec, n, treated_pids, control_pids, trimmed_cohorts)])
filing_acq_rows[, acquirer_type := label_map_acq[spec]]
filing_acq_rows <- filing_acq_rows[, .(acquirer_type, treated_pids, control_pids, stacked_rows = n, trimmed_cohorts)]

core_2plus_t1 <- filing_core[spec == "core_2plus" & et == 1L, estimate]
core_5plus_t1 <- filing_core[spec == "core_5plus" & et == 1L, estimate]
core_10plus_t1 <- filing_core[spec == "core_10plus" & et == 1L, estimate]
high_filer_t2 <- filing_acq[spec == "highfiler_portfolio_10plus_otherunits" & et == 2L, estimate]
low_filer_t2 <- filing_acq[spec == "lowfiler_portfolio_10plus_otherunits" & et == 2L, estimate]
high_filer_se_t2 <- filing_acq[spec == "highfiler_portfolio_10plus_otherunits" & et == 2L, std_error]
low_filer_se_t2 <- filing_acq[spec == "lowfiler_portfolio_10plus_otherunits" & et == 2L, std_error]
filing_rate_cap <- acq_cutoffs[1, filing_rate_cap]
loo_unit_cutoff <- acq_cutoffs[1, meaningful_loo_unit_years_cutoff]
high_filer_cutoff <- acq_cutoffs[1, high_filer_rate_cutoff]
```

# Overview

This note reports the streamlined annual transfer-evictions specification. The main outcome is `filing_rate = num_filings / total_units` in a full building-year panel from `r sample_year_min` to `r sample_year_max`, with single-transfer treated buildings compared against buildings never transferred in the RTT data. All annual event studies are estimated on `t \in [r event_window_min, r event_window_max]`, with omitted event time `t = r event_ref_period`.

For filing outcomes, the main specification is a weighted stacked event study:

$$
y_{i a t} = \sum_{k \in \{-3,-1,0,1,2,3\}} \beta_k \mathbf{1}\{\mathrm{rel\_time}_{ia}=k\}
          + \alpha_{ia} + \lambda_{at} + \varepsilon_{iat},
$$

estimated on a cohort-stacked panel with weights `q_weight × total_units`, where `q_weight`
is the Wing et al. corrective control weight and `\alpha_{ia}` and `\lambda_{at}` are
stack-specific parcel and year fixed effects. Non-filing outcomes continue to use the
annual `PID + year` event-study design on the same `-3:3` window.

Operationally, `q_weight` corrects the fact that the same never-transferred controls are
reused in multiple cohort stacks. Multiplying by `total_units` then makes the corrected
stacked estimator unit-weighted, so the filing results are a weighted average over unit
exposure rather than a simple parcel average.

The annual surface has been pruned to four blocks:

- filing-rate event studies
- occupancy, resident-composition, complaint, and permit outcomes
- rent outcomes using the unified and safe series
- rental-evidence event studies for `1-unit` and `2+ unit` buildings

Portfolio filing types are computed using the helper logic from the production script, with portfolio size and filing rates defined using all holdings, including `1-unit` buildings. The filing and neighborhood-outcome regressions then restrict the estimation sample as needed.

The acquirer bins are:

- `Single-purchase`: leave-one-out portfolio exposure is exactly `0` unit-years.
- `Small portfolio`: leave-one-out portfolio exposure is positive but below `r fmt_int(loo_unit_cutoff)` unit-years.
- `Low-filer portfolio`: leave-one-out portfolio exposure is at least `r fmt_int(loo_unit_cutoff)` unit-years and the leave-one-out filing rate is below `r fmt_num(high_filer_cutoff, 2)` filings per unit-year.
- `High-filer portfolio`: leave-one-out portfolio exposure is at least `r fmt_int(loo_unit_cutoff)` unit-years and the leave-one-out filing rate is at least `r fmt_num(high_filer_cutoff, 2)` filings per unit-year.

For the filing-rate outcome and for the leave-one-out filing-rate bins, annual filing rates are capped at `r fmt_num(filing_rate_cap, 2)` filings per unit-year before aggregation.

# Main Filing Results

The main filing figures now use the weighted stacked estimator directly. The filing sample grid separates `1-unit` properties from the multifamily stock. The main justification for the `2+ unit` analysis sample is that the `2+` and `5+` estimates are close, while `1-unit` properties are shown separately as the single-family contrast and the `10+` cut is treated as a stricter appendix validation rather than the main specification.

At `t = +1`, the filing-rate coefficient is `r fmt_num(core_2plus_t1, 4)` for `2+ units`, `r fmt_num(core_5plus_t1, 4)` for `5+ units`, and `r fmt_num(core_10plus_t1, 4)` for `10+ units`.

```{r filing-sample-table}
kable(
  filing_sample_rows,
  col.names = c("Sample", "Treated transfers", "Control PIDs", "Stacked rows"),
  format.args = list(big.mark = ","),
  caption = "Sample sizes for the streamlined annual filing-rate event studies"
) |>
  kable_styling(latex_options = c("hold_position"))
```

```{r filing-core-plot, fig.cap="Weighted stacked annual filing-rate event study by sample restriction. The main figure overlays 1-unit, 2+, 5+, and 5+ rental-evidence samples; 10+ remains a stricter appendix check in the tables."}
must_graphic(file.path(fig_dir, "rtt_annual_filing_core.png"))
```

```{r filing-core-table, results='asis'}
include_tex_table(file.path(out_dir, "annual_filing_core_etable.tex"), size = "scriptsize")
```

```{r filing-core-summary}
core_summary <- event_summary(
  filing_core,
  spec_labels = label_map_core[c(
    "core_1unit",
    "core_2plus",
    "core_2plus_rental_evidence",
    "core_5plus",
    "core_5plus_rental_evidence",
    "core_10plus",
    "core_10plus_rental_evidence"
  )]
)
setnames(core_summary, c("Sample", "t+1", "t+2", "t+3"))
kable(
  core_summary,
  caption = "Selected filing-rate coefficients from the streamlined sample grid"
) |>
  kable_styling(latex_options = c("hold_position"))
```

# Filing Heterogeneity by Acquirer Type

The main heterogeneity split uses four acquirer types:

- `High-filer portfolio`
- `Low-filer portfolio`
- `Small portfolio`
- `Single-purchase`

These categories are defined from the helper-function leave-one-out portfolio measures, while the regression itself is restricted to `2+ unit` buildings. In the current annual weighted stacked outputs, the `t = +2` coefficient is `r fmt_num(high_filer_t2, 4)` for high-filer portfolios and `r fmt_num(low_filer_t2, 4)` for low-filer portfolios.

The standard errors differ sharply across these bins. At `t = +2`, the high-filer estimate has standard error `r fmt_num(high_filer_se_t2, 4)` versus `r fmt_num(low_filer_se_t2, 4)` for low-filer acquirers, which largely reflects the much smaller treated sample for high-filer acquisitions.

```{r filing-acq-sample-table}
kable(
  filing_acq_rows,
  col.names = c("Acquirer type", "Treated transfers", "Control PIDs", "Stacked rows", "Trimmed cohorts"),
  format.args = list(big.mark = ","),
  caption = "Weighted stacked 2+ filing-rate sample sizes by acquirer type"
) |>
  kable_styling(latex_options = c("hold_position"))
```

```{r filing-acq-plot, fig.cap="Annual filing-rate event study for 2+ unit buildings, split by acquirer filing type. Controls are never-transferred buildings in the same 2+ unit sample."}
must_graphic(file.path(fig_dir, "rtt_annual_filing_acq_2plus.png"))
```

```{r filing-acq-table, results='asis'}
include_tex_table(file.path(out_dir, "annual_filing_acq_2plus_etable.tex"), size = "scriptsize")
```

```{r filing-acq-summary}
acq_summary <- event_summary(
  filing_acq,
  spec_labels = label_map_acq
)
setnames(acq_summary, c("Acquirer type", "t+1", "t+2", "t+3"))
kable(
  acq_summary,
  caption = "Selected 2+ unit filing-rate coefficients by acquirer type"
) |>
  kable_styling(latex_options = c("hold_position"))
```

# Occupancy, Demographics, Complaints, and Permits

These outcomes are estimated on the `2+ unit` sample and split by the same acquirer-type bins as the filing regressions. The output surface here is intentionally narrower than the earlier report: the focus is occupancy, resident composition, complaints, and permits.

```{r occupancy-plot, fig.cap="Occupancy-rate event study for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_occupancy_2plus.png"))
```

```{r occupancy-table, results='asis'}
include_tex_table(file.path(out_dir, "annual_occupancy_2plus_etable.tex"), size = "scriptsize")
```

```{r race-black-plot, fig.cap="Share Black residents for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_pct_black_2plus.png"))
```

```{r race-latino-plot, fig.cap="Share Latino residents for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_pct_latino_2plus.png"))
```

```{r race-white-plot, fig.cap="Share White residents for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_pct_white_2plus.png"))
```

```{r race-asian-plot, fig.cap="Share Asian residents for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_pct_asian_2plus.png"))
```

```{r permit-plot, fig.cap="Permit-rate event study for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_permit_rate_2plus.png"))
```

```{r complaint-plot, fig.cap="Complaint-rate event study for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_complaint_rate_2plus.png"))
```

# Rent Outcomes

The rent analysis is run on all units, but treated buildings are required to have both pre- and post-acquisition support in the relevant rent measure. The report keeps both the unified rent series and the safe single-source series.

```{r rent-core-plot, fig.cap="Log median rent event study, all units, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_rent_core.png"))
```

```{r rent-core-table, results='asis'}
include_tex_table(file.path(out_dir, "annual_rent_core_etable.tex"), size = "scriptsize")
```

```{r rent-safe-plot, fig.cap="Log median rent (safe single-source series) event study, all units, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_rent_safe_core.png"))
```

```{r rent-safe-table, results='asis'}
include_tex_table(file.path(out_dir, "annual_rent_safe_core_etable.tex"), size = "scriptsize")
```

# Rental Evidence

These regressions show the probability of observed rental evidence separately for `1-unit` and `2+ unit` buildings. This is the direct check on the concern that transfers mechanically enter properties into the observed rental market.

```{r rental-evidence-1unit-plot, fig.cap="Probability of rental evidence for 1-unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_rental_evidence_1unit.png"))
```

```{r rental-evidence-1unit-table, results='asis'}
include_tex_table(file.path(out_dir, "annual_rental_evidence_1unit_etable.tex"), size = "scriptsize")
```

```{r rental-evidence-2plus-plot, fig.cap="Probability of rental evidence for 2+ unit buildings, overall and by acquirer filing type."}
must_graphic(file.path(fig_dir, "rtt_annual_rental_evidence_2plus.png"))
```

```{r rental-evidence-2plus-table, results='asis'}
include_tex_table(file.path(out_dir, "annual_rental_evidence_2plus_etable.tex"), size = "scriptsize")
```

# Appendix: Output Inventory

The streamlined annual writeup now depends on the following output families:

- `annual_filing_core_*`
- `annual_filing_acq_2plus_*`
- `annual_occupancy_2plus_*`
- `annual_pct_*_2plus_*`
- `annual_permit_rate_2plus_*`
- `annual_complaint_rate_2plus_*`
- `annual_rent_core_*`
- `annual_rent_safe_core_*`
- `annual_rental_evidence_1unit_*`
- `annual_rental_evidence_2plus_*`

Legacy annual outputs and scratch stacked CSVs are no longer required for this document.
